---
title: "all_final"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(plyr)
library(tidyr)
library(haven)
library(labelled)
library(gmodels)
library(ggplot2)
library(survey)
library(jtools)
library(car)
library(interactions)
library(ggstance)
options("jtools-digits" = 8)
```

# Inport and Tidy ANES data

```{r}
anes2016all <- read_dta("anes2016.dta")

# select needed economic variables
econ2016 <- anes2016all %>%
  select(c(
    caseid,
    V160101, # Pre election weight, full sample
    V160102, # Post election weight, full sample
    stfips, # STATE FIPS CODE
    stabbrev, # STATE ABBREVIATION
    congdist, # CONGRESSIONAL DISTRICT NUMBER
    ahowlong, # how long at current address 1 = 0-1 years ... 9 = 30+ years
    libcon, # POLITICAL ID (FORCED): 6 = STRONG CONSERVATIVE ... 0 = STRONG LIBERAL
    partyid, # PARTISAN ID: 6 = STRONG REP ... 0 = STRONG DEM
    age, # RESPONDENT AGE IN YEARS
    V161267x, # PRE: SUMMARY - RESPONDENT AGE GROUP
    V161270, # PRE: HIGHEST LEVEL OF EDUCATION
    race, # 1 = WHITE, 2 = BLACK, 3 = ASIAN, 4 = NATIVE, 5 = HISPANIC, 6 = OTHER
    gender, # 1 = R IS A WOMAN, 0 = MAN
    govservice, # GOV SERVICES SCALE: 6 = GOV SHOULD PROVIDE MORE SERVICES
    medinsur, # MEDICAL INSURANCE SCALE: 6 = GOV INSUANCE ... 0 = PRIVATE INSURANCE
    fedgun, # 2 = GUN PURCHASE EASIER, 1 = THE SAME, 0 = GUN PURCHASE MORE DIFFICULT
    govjob, # GOV JOB SCALE: 6 = GOV GUARANTEES JOBS ... 0 = GET JOBS ON OWN
    govblacks, # AID TO BLACKS SCALE: 6 = GOV SHOULD HELP BLACKS ... 0 = BLACKS HELP SELVES
    ssocsec, # 1 = INCREASED SPENDING ON SOCSEC, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sschools, # 1 = INCREASED SPENDING ON SCHOOLS, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sscience, # 1 = INCREASED SPENDING ON SCIENCE, 0 = KEEP SAME, -1 DECREASED SPENDING
    swelfare, # 1 = INCREASED SPENDING ON WELFARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    schildcare, # 1 = INCREASED SPEND ON CHILD CARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    spoor, # 1 = INCREASED SPEND ON POOR, 0 = KEEP SAME, -1 = DECREASED SPENDING
    senviron, # 1 = INCREASED SPEND ON ENVIRONMENT, 0 = KEEP SAME, -1 = DECREASED,
    gwaction, # 6 = GOV SHOULD BE DOING GREAT DEAL MORE FOR GLOBAL WARMING ... 0 = LESS
    govinequality, # 2 = R SUPPORT GOV EFFORTS TO REDUCE INEQUALITY, 1 = NEUTRAL, 0 = OPPOSE
    shealthcare7, # 6 = SUPPORT STRONG INCREASE IN HEALTH CARE SPEND, 0 = STRONG DECREASE
    taxmillion, # 2 = SUPPORTS INCREASING TAXES ON MILLIONAIRES, 1 = NEUTRAL, 0 = OPPOSE
    govprob, # 1 = gov doing too much, 0 = problems are bigger
    fmarket, # 1 = FREE MARKET CAN HANDLE PROBLEMS, 0 = GOV NEEDED TO SOLVE PROBLEMS
    govless, # 1 = LESS GOV THE BETTER, 0 = GOV SHOULD DO MORE THINGS
    gregbus, # 4 = A GREAT DEAL OF REGULATION IS GOOD FOR SOCIETY ... 0 = NONE AT ALL
    emorechance, # It is big problem if some have more chances than others (4 = strongly agree)
    eworry, # USA would be better off if we worried less about equality (4 = strongly agree)
    eequalopp, # Our society should do all possible for equal opportunity (4 = strongly agree)
    efair, # If people treated more equal USA would have fewer problems (4 = strongly agree)
    madjust, # We should adjust morality to changing world (4 = strongly agree)
    mbreakdown, # Newer lifestyles contributing to breakdown of society (4 = strongly agree)
    mtolerant, # We should be tolerant of those with different morality (4 = strongly agree)
    mtraditional, # Country better with emphasis on traditional family ties (4 = strongly agree)
    glservice, # 5 = require service for gay couples ... 0 = refuse service
    transbath, # 5 = trans use bathroom of choice ... 0 = use bathroom of gender born with
    gaydiscrim, # 3 = strongly favor antidiscrimination laws for gays ... 0 = strongly oppose
    equalpay, # 6 =  R strongly supports equal pay for equal work; . . . ; 0 = strongly oppose
    freethink # = R strongly agrees USA needs more free thinks; . . . ; 0 = strongly disagrees
  ))


# combine weights
econ2016 <- econ2016 %>%
  mutate(weight = ifelse(V160101 == 0, V160102, V160101))

# remove haven labeling from relevant variables
econ2016$V161267x <- remove_attributes(econ2016$V161267x, "format.spss")
econ2016$V161270 <- remove_attributes(econ2016$V161270, "format.spss")

econ2016$V161267x <- as.numeric(econ2016$V161267x)
econ2016$V161270 <- as.numeric(econ2016$V161270)

# recode demographic variables for analysis
econ2016 <- econ2016 %>%
  transform(age2 = age^2) %>%
  mutate(agegroup = recode(V161267x,
                           `1` = 0, # age group 18-20 -> 18-24
                           `2` = 0, # age group 21-24 -> 18-24
                           `3` = 1, # age group 25-29 -> 25-34
                           `4` = 1, # age group 30-34 -> 25-34
                           `5` = 2, # age group 35-39 -> 35-44
                           `6` = 2, # age group 40-44 -> 35-44
                           `7` = 3, # age group 45-49 -> 45-54
                           `8` = 3, # age group 50-54 -> 45-54
                           `9` = 4, # age group 55-59 -> 55-64
                           `10` = 4, # age group 60-64 -> 55-64
                           `11` = 5, # age group 65-69 -> 65-74
                           `12` = 5, # age group 70-74 -> 65-74
                           `13` = 6 # age group 75 or older
                           )) %>%
  mutate(highested = recode(V161270,
                            `1` = 0, # education less than 1st -> no high school diploma
                            `2` = 0, # education 1-4th grade -> no high school diploma
                            `3` = 0, # education 5-6th grade -> no high school diploma
                            `4` = 0, # education 7-8th grade -> no high school diploma
                            `5` = 0, # 9th grade -> no high school diploma
                            `6` = 0, # 10th grade -> no high school diploma
                            `7` = 0, # 11th grade -> no high school diploma
                            `8` = 0, # 12th grade no diploma -> no high school diploma
                            `9` = 1, # high school diploma or equivalent
                            `90` = 1, # other given as high school graduate -> hs diploma 
                            `10` = 2, # some college but no digree
                            `11` = 3, # associate degree 
                            `12` = 3, # associate degree
                            `13` = 4, # Bachelors degree
                            `14` = 5, # Master's degree
                            `15` = 6, # professional degree -> doctorate or professional degree
                            `16` = 6 # doctorate degree -> doctorate or professional degree
                            )) %>%
  mutate(race = recode(race, 
                       `1` = 0, # white
                       `2` = 1, # black
                       `3` = 2, # asian
                       `4` = 3, # native american
                       `5` = 4, # hispanic,
                       `6` = 5 # other
                       ))

econ2016 <- econ2016 %>%
#  filter(agegroup >= 0) %>%
  filter(highested >= 0)

# remove NA
 econ2016 <- na.omit(econ2016)

# reverse code so high values indicate more liberal issue positions 
econ2016 <- econ2016 %>%
  mutate(libcon = recode(libcon, #recode so 6 = strong liberal and 0 = strong conservative
                         `0` = 6,
                         `1` = 5,
                         `2` = 4, 
                         `4` = 2,
                         `5` = 1, 
                         `6` = 0
                          )) %>%
  mutate(partyid = recode(partyid, #recode so 6 = strong Democrat and 0 = strong Republican
                          `0` = 6,
                          `1` = 5,
                          `2` = 4, 
                          `4` = 2,
                          `5` = 1, 
                          `6` = 0
                          ))  %>%
  mutate(fedgun = recode(fedgun, #recode -> 2 = gun purchase more difficult and 0 = gun purchase more easy
                         `0` = 2,
                         `2` = 0
                          )) %>%
  mutate(ssocsec = recode(ssocsec, #recode so 2 = more spending, 1 = stay the same, 0 = decrease spending
                          `1` = 2,
                          `0` = 1,
                          `-1` = 0
                          )) %>%
  mutate(sschools = recode(sschools, #recode so 2 = increased spending, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(sscience = recode(sscience, #recode 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(swelfare = recode(swelfare, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(schildcare = recode(schildcare, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(spoor = recode(spoor, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(senviron = recode(senviron, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(govprob = recode(govprob,
                          `1` = 0,
                          `0` = 1
                          )) %>%
  mutate(fmarket = recode(fmarket, #reverse code 1 = gov needed to solve problems, 0 = free market can handle
                          `1` = 0,
                          `0` = 1
                          )) %>%
  mutate(govless = recode(govless, #reverse code 1 = gov should do more things, 0 = less gov the better
                          `1` = 0,
                          `0` = 1
                          ))
    

#create factor score by dividing each column by the number of questions to give a value between 0 and 1
econ2016 <- econ2016 %>%
  mutate(govservice1 = govservice / 6) %>%
  mutate(medinsur1 = medinsur / 6) %>%
  mutate(fedgun1 = fedgun / 2) %>%
  mutate(govjob1 = govjob / 6) %>%
  mutate(govblacks1 = govblacks / 6) %>%
  mutate(ssocsec1 = ssocsec / 2) %>%
  mutate(sschools1 = sschools / 2) %>%
  mutate(sscience1 = sscience / 2) %>%
  mutate(swelfare1 = swelfare / 2) %>%
  mutate(schildcare1 = schildcare / 2) %>%
  mutate(spoor1 = spoor / 2) %>%
  mutate(senviron1 = senviron / 2) %>%
  mutate(gwaction1 = gwaction / 6) %>%
  mutate(govinequality1 = govinequality / 2) %>%
  mutate(shealthcare71 = shealthcare7 / 6) %>%
  mutate(taxmillion1 = taxmillion / 2) %>%
  mutate(govprob1 = govprob / 1) %>%
  mutate(fmarket1 = fmarket / 1) %>%
  mutate(govless1 = govless / 1) %>%
  mutate(gregbus1 = gregbus / 4)


#add all together to create single factor score for economic dimension
 econ2016 <- econ2016 %>%
  dplyr::mutate(fecon20 = 
           govservice1 + 
           medinsur1 +
           fedgun1 +
           govjob1 + 
           govblacks1 + 
           ssocsec1 +
           sschools1 +
           sscience1 +
           swelfare1 +
           schildcare1 +
           spoor1 +
           senviron1 +
           gwaction1 +
           govinequality1 +
           shealthcare71 +
           taxmillion1 +
           govprob +
           fmarket1 +
           govless1 +
           gregbus1
           ) %>%
     dplyr::mutate(fecon10 = 
           govservice1 + 
           medinsur1 +
           govjob1 + 
           ssocsec1 +
           sschools1 +
           sscience1 +
           swelfare1 +
           schildcare1 +
           spoor1 +
           senviron1
           )

# check range of factor score to be 0 (most conservative) to 20 (most liberal)
range(econ2016$fecon10)
range(econ2016$fecon20)

# select needed variables
econ2016 <- econ2016 %>%
  select("caseid", 
         "weight", 
         "stfips", 
         "stabbrev", 
         "congdist",
         "libcon",
         "partyid",
         "ahowlong",
         "age",
         "age2",
         "agegroup",
         "highested", 
         "race", 
         "gender", 
         "fecon20",
         "fecon10",
         "emorechance", 
         "eequalopp",
         "mtolerant",
         "mtraditional",
         )
```

# Import and Tidy Population Density Data from ArcGIS Hub
[Source](https://hub.arcgis.com/datasets/ff48bbae433442a38f6c635b8c7baf72_0/data?geometry=11.844%2C-0.129%2C102.899%2C76.650)
```{r}
# create data frame
geo2016 <- X2016_Population_Density_by_Congressional_District %>%
  select(c(
    OBJECTID,
    ID,
    NAME, # NAME OF THE CONGRESSIONAL DISTRICT
    ST_ABBREV,
    TOTPOP_CY, # TOTAL POPULATION OF DISTRICT IN 2016
    POPDENS_CY, # POPULATION DENSITY OF DISTRICT IN 2016
    POPGRW10CY # POPULATION GROWTH RATE 2010 - 2016
  ))

# remove alphabetic characters to give only district number
geo2016$NAME <- gsub("[a-zA-Z ]", "", geo2016$NAME)

# remove dash in district number
geo2016$NAME <- gsub("\\-", "", geo2016$NAME)

# make district number vector numeric
 geo2016$NAME <- as.double(geo2016$NAME)

# add leading zeros to district number
geo2016$NAME <- sprintf("%02d", geo2016$NAME)

# turn ST_ABBREV into a character variable
geo2016$ST_ABBREV <- as.character(geo2016$ST_ABBREV)

# combine ST_ABBREV and NAME to form CD (consistent with other data set)
geo2016 <- geo2016 %>%
  unite(col = "CD", ST_ABBREV:NAME, sep = "-")

# make CD a character variable
geo2016$CD <- as.character(geo2016$CD)

# turn POPDENS_CY into a numeric
geo2016$POPDENS_CY <- as.numeric(geo2016$POPDENS_CY)
```

# Import and Tidy Election Data from the Daily Kos
* since arguing it is about geographic location, use local election results to determine the red/blue culture of the area - need to find justification
* used data on election results for congressional districts used in 2016 election because that is the year of the ANES data
* make dummy variable -- 1 means majority voted blue 
* also make a dummy variable for presidential vote

**NEED TO MAKE BETTER PRES_BLUEVOTE CALCULATION -- FIGURE OUT HOW TO MUTATE SO IF CLINTON > TRUMP, THEN 1**

```{r}
dailykos_pres <- read_csv("Daily Kos Elections 2008, 2012 & 2016 presidential election results for congressional districts used in 2016 elections - Results.csv", 
                     skip = 1)

# make variable for % Clinton vote into blue vote

election <- dailykos %>%
  mutate(pres_bluevote = ifelse(Clinton >= 50, 1, 0)) %>%
  mutate(local_bluevote = ifelse(Party == "(D)", 1, 0))

# select needed variables
election <- election %>%
  select("CD", "pres_bluevote", "local_bluevote", "Clinton")
```

# Combine Data Sets

## Daily Kos + ArcGIS
```{r}
# combine data sets using CD variable -- same format
combine2016 <- merge(geo2016, election, by = c("CD"))
```

## Add ANES data
```{r}
# alter formatting of CD variable to be like ANES
combine2016 <- combine2016 %>%
  separate("CD", (c("stabbrev", "congdist0")), sep = "-")

# add leading 0 into ANES
econ2016$congdist0 <- str_pad(econ2016$congdist, width = 2, side = "left", pad = "0")

# combine two data sets
combine2016 <- merge(econ2016, combine2016, by = c("stabbrev", "congdist0"))
```

# Descriptive Statistics of Respondents
```{r}
combine2016 %>%
  group_by(factor(partyid)) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

combine2016 %>%
  group_by(libcon) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

combine2016 %>%
  group_by(race) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

combine2016 %>%
  group_by(gender) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

combine2016 %>%
  group_by(agegroup) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

combine2016 %>%
  group_by(highested) %>%
  dplyr::summarise(n = n()) %>%
  mutate(freq = n / sum(n))

combine2016 %>%
  group_by(partyid) %>%
  dplyr::summarise(n = n(), mean = mean(fecon10), sd = sd(fecon10))

combine2016 %>%
  group_by(libcon) %>%
  dplyr::summarise(n = n(), mean = mean(fecon10), sd = sd(fecon10))
```

# Distribution of Operational Ideology
```{r}
ggplot(combine2016, aes(x = fecon10, color = factor(partyid))) +
  geom_density() +
  scale_x_continuous(name = 'Econ Preferences') +
  scale_color_discrete(name = 'Party ID', labels = c("Strong Republican", "Republican", "Lean Republican", "Independent", "Lean Democrat", "Democrat", "Strong Democrat"))

ggplot(combine2016, aes(x = fecon10, color = factor(libcon))) +
  geom_density() +
  scale_x_continuous(name = 'Econ Preferences') +
  scale_color_discrete(name = 'Ideological ID', labels = c("Extremely Conservative", "Conservative", "Moderate Conservative", "Moderate", "Moderate Liberal", "Liberal", "Extremely Liberal"))
```


# Make separate data sets for each identity

```{r}
# Ideological Identity
st_lib <- filter(combine2016, libcon == 6) # STRONG LIBERAL

lib <- filter(combine2016, libcon == 5) # LIBERAL

m_lib <- filter(combine2016, libcon == 4) # MODERATE LIBERAL

mod <- filter(combine2016, libcon == 3) # MODERATE

m_con <- filter(combine2016, libcon == 2) # MODERATE CONSERVATIVE

con <- filter(combine2016, libcon == 1) # CONSERVATIVE

st_con <- filter(combine2016, libcon == 0) # STRONG CONSERVATIVE

# Party ID
st_dem <- filter(combine2016, partyid == 6) # STRONG DEMOCRAT

dem <- filter(combine2016, partyid == 5) # DEMOCRAT

m_dem <- filter(combine2016, partyid == 4) # MODERATE DEMOCRAT

ind <- filter(combine2016, partyid == 3) # MODERATE

m_rep <- filter(combine2016, partyid == 2) # MODERATE REPUBLICAN

rep <- filter(combine2016, partyid == 1) # REPUBLICAN

st_rep <- filter(combine2016, partyid == 0) # STRONG REPUBLICAN
```

# Regressions

## Overall-Party ID
```{r}
overall_design <- svydesign(ids = ~1, weights = ~weight, data = combine2016)

overall.party_regress <- svyglm(formula = fecon10 ~ partyid, design = overall_design)
summ(overall.party_regress,
     center = TRUE)

stats:::anova.glm(overall.party_regress, test = "F")

overall.party_regress2 <- svyglm(formula = fecon10 ~ POPDENS_CY, design = overall_design)
summ(overall.party_regress2, 
     center = TRUE)

stats:::anova.glm(overall.party_regress2, test = "F")

overall.party_regress3 <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                                 design = overall_design)
summ(overall.party_regress3,
     center = TRUE)

stats:::anova.glm(overall.party_regress3, test = "F")

sim_slopes(overall.party_regress3, 
                                pred = POPDENS_CY, 
                                modx = partyid, 
                                modx.values = c(0, 1, 2, 3, 4, 5, 6), 
                                centered = "all", 
                                data = combine2016)
```

## Strong Democrat
```{r}
stdem_design <- svydesign(ids = ~1, weights = ~weight, data = st_dem)

stdem_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                        design = stdem_design)
summ(stdem_regress,
     center = TRUE)
```

## Democrat
```{r} 
dem_design <- svydesign(ids = ~1, weights = ~weight, data = dem)

dem_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                      design = dem_design)
summ(dem_regress,
     center = TRUE)
```

## Idependent-Democrat
```{r}
ind.dem_design <- svydesign(ids = ~1, weights = ~weight, data = m_dem)

ind.dem_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                          design = ind.dem_design)
summ(ind.dem_regress,
     center = TRUE)
```

## Independent
```{r}
ind_design <- svydesign(ids = ~1, weights = ~weight, data = ind)

ind_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                      design = ind_design)
summ(ind_regress,
     center = TRUE)
```

## Independent-Republican
```{r}
ind.rep_design <- svydesign(ids = ~1, weights = ~weight, data = m_rep)

ind.rep_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                          design = ind.rep_design)
summ(ind.rep_regress,
     center = TRUE)
```

## Republican
```{r}
rep_design <- svydesign(ids = ~1, weights = ~weight, data = rep)

rep_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                      design = rep_design)
summ(rep_regress,
     center = TRUE)
```

## Strong Republican
```{r}
strep_design <- svydesign(ids = ~1, weights = ~weight, data = st_rep)

strep_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * partyid, 
                        design = strep_design)
summ(strep_regress,
     center = TRUE)
```

## Linear trend lines
```{r}
party_eq1=function(x){coef(stdem_regress)[2]*x+coef(stdem_regress)[1]}
party_eq2=function(x){coef(dem_regress)[2]*x+coef(dem_regress)[1]}
party_eq3=function(x){coef(ind.dem_regress)[2]*x+coef(ind.dem_regress)[1]}
party_eq4=function(x){coef(ind_regress)[2]*x+coef(ind_regress)[1]}
party_eq5=function(x){coef(ind.rep_regress)[2]*x+coef(ind.rep_regress)[1]}
party_eq6=function(x){coef(rep_regress)[2]*x+coef(rep_regress)[1]}
party_eq7=function(x){coef(strep_regress)[2]*x+coef(strep_regress)[1]}

ggplot(combine2016, aes(y = fecon10, x = POPDENS_CY, color = factor(partyid)))+
  geom_point(size = 2, stroke = 0, shape = 16, alpha = 0.7) +
  stat_function(fun = party_eq1, geom="line", color = scales::hue_pal()(7)[1], aes(color = "Strong Democrat")) +
  stat_function(fun = party_eq2, geom="line", color = scales::hue_pal()(7)[2], aes(color = "Democrat")) +
  stat_function(fun = party_eq3, geom="line", color = scales::hue_pal()(7)[3], aes(color = "Lean Democrat")) +
  stat_function(fun = party_eq4, geom = "line", color = scales::hue_pal()(7)[4], aes(color = "Independent")) +
  stat_function(fun = party_eq5, geom = "line", color = scales::hue_pal()(7)[5], aes(color = "Lean Republican")) +
  stat_function(fun = party_eq6, geom = "line", color = scales::hue_pal()(7)[6], aes(color = "Republican")) +
  stat_function(fun = party_eq7, geom = "line", color = scales::hue_pal()(7)[7], aes(color = "Strong Republican")) +
  scale_color_discrete(labels = c("Strong Democrat", "Democrat", "Lean Democrat", "Independent", "Lean Republican", "Republican", "Strong Republican")) +
  labs(x = "Population Density",
       y = "Issue Positions",
       color = "Party ID") +
  ylim(0, 10)
```

-------------------------------------------------------
## Overall-Ideological ID
```{r}
overall_design <- svydesign(ids = ~1, weights = ~weight, data = combine2016)

overall.id_regress <- svyglm(formula = fecon10 ~ libcon, design = overall_design)
summ(overall.id_regress,
     center = TRUE)

stats:::anova.glm(overall.id_regress, test = "F")

overall.id_regress2 <- svyglm(formula = fecon10 ~ POPDENS_CY, design = overall_design)
summ(overall.id_regress2, 
     center = TRUE)

stats:::anova.glm(overall.id_regress2, test = "F")

overall.id_regress3 <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                              design = overall_design)
summ(overall.id_regress3,
     center = TRUE)

stats:::anova.glm(overall.id_regress3, test = "F")

sim_slopes(overall.id_regress3, 
           pred = POPDENS_CY, 
           modx = libcon, 
           modx.values = c(0, 1, 2, 3, 4, 5, 6),
           centered = "all", 
           data = combine2016)

```

## Strong Liberal
```{r}
stlib_design <- svydesign(ids = ~1, weights = ~weight, data = st_lib)

stlib_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = stlib_design)
summ(stlib_regress,
     center = TRUE)
```

## Liberal
```{r}
lib_design <- svydesign(ids = ~1, weights = ~weight, data = lib)

lib_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = lib_design)
summ(lib_regress,
     center = TRUE)
```

## Moderate Liberal
```{r}
mlib_design <- svydesign(ids = ~1, weights = ~weight, data = m_lib)

mlib_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = mlib_design)
summ(mlib_regress,
     center = TRUE)
```

## Moderate
```{r}
mod_design <- svydesign(ids = ~1, weights = ~weight, data = mod)

mod_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = mod_design)
summ(mod_regress,
     center = TRUE)
```

## Moderate Conservative
```{r}
mcon_design <- svydesign(ids = ~1, weights = ~weight, data = m_con)

mcon_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = mcon_design)
summ(mcon_regress,
     center = TRUE)
```

## Conservative
```{r}
con_design <- svydesign(ids = ~1, weights = ~weight, data = con)

con_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = con_design)
summ(con_regress,
     center = TRUE)
```
## Strong Conservative
```{r}
stcon_design <- svydesign(ids = ~1, weights = ~weight, data = st_con)

stcon_regress <- svyglm(formula = fecon10 ~ POPDENS_CY * libcon, 
                        design = stcon_design)
summ(stcon_regress,
     center = TRUE)
```


# Graph Regression Outputs
## Ideological Identification
```{r}
id_eq1=function(x){coef(stlib_regress)[2]*x+coef(stlib_regress)[1]}
id_eq2=function(x){coef(lib_regress)[2]*x+coef(lib_regress)[1]}
id_eq3=function(x){coef(mlib_regress)[2]*x+coef(mlib_regress)[1]}
id_eq4=function(x){coef(mod_regress)[2]*x+coef(mod_regress)[1]}
id_eq5=function(x){coef(mcon_regress)[2]*x+coef(mcon_regress)[1]}
id_eq6=function(x){coef(con_regress)[2]*x+coef(con_regress)[1]}
id_eq7=function(x){coef(stcon_regress)[2]*x+coef(stcon_regress)[1]}

ggplot(combine2016, aes(y = fecon10, x = POPDENS_CY, color = factor(libcon)))+
  geom_point(size = 2, stroke = 0, shape = 16, alpha = 0.7) +
  stat_function(fun = id_eq1, geom="line", color = scales::hue_pal()(7)[1], aes(color = "Extreme Liberal")) +
  stat_function(fun = id_eq2, geom="line", color = scales::hue_pal()(7)[2], aes(color = "Liberal")) +
  stat_function(fun = id_eq3, geom="line", color = scales::hue_pal()(7)[3], aes(color = "Moderate Liberal")) +
  stat_function(fun = id_eq4, geom = "line", color = scales::hue_pal()(7)[4], aes(color = "Moderate")) +
  stat_function(fun = id_eq5, geom = "line", color = scales::hue_pal()(7)[5], aes(color = "Moderate Conservative")) +
  stat_function(fun = id_eq6, geom = "line", color = scales::hue_pal()(7)[6], aes(color = "Conservative")) +
  stat_function(fun = id_eq7, geom = "line", color = scales::hue_pal()(7)[7], aes(color = "Extreme Conservative")) +
  scale_color_discrete(labels = c("Extreme Liberal", "Liberal", "Moderate Liberal", "Moderate", "Moderate Conservative", "Conservative", "Extreme Conservative")) +
  labs(x = "Population Density",
       y = "Issue Positions",
       color = "Ideological ID") +
  ylim(0, 10)
```


