---
title: "Consolidate with Factor Score and Pop Dens"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(tidyr)
library(haven)
library(gmodels)
library(ggplot2)
```

# Notes
* future research can be performed using more comprehensive measures of an area's population, like that of City Lab.


# Import And Tidy Data Sets

## ANES 2016 Survey Data
```{r}
anes2016all <- read_dta("anes2016.dta")

# select needed economic variables
econ2016 <- anes2016all %>%
  select(c(
    caseid,
    stfips, # STATE FIPS CODE
    stabbrev, # STATE ABBREVIATION
    congdist, # CONGRESSIONAL DISTRICT NUMBER
    libcon, # POLITICAL ID (FORCED): 6 = STRONG CONSERVATIVE ... 0 = STRONG LIBERAL
    partyid, # PARTISAN ID: 6 = STRONG REP ... 0 = STRONG DEM
    V161267x, # PRE: SUMMARY - RESPONDENT AGE GROUP
    educ, # 1 = LESS THAN HIGH SCHOOL ... 8 = DOCTORATE OR PROFESSIONAL
    V161270, # PRE: HIGHEST LEVEL OF EDUCATION
    race, # 1 = WHITE, 2 = BLACK, 3 = ASIAN, 4 = NATIVE, 5 = HISPANIC, 6 = OTHER
    hispanic, # 1 = R IS HISPANIC, 0 = OTHERWISE
    white, # 1 = R IS WHITE NON-HISPANIC, 0 = OTHERWISE
    white1, # 1 = R IS WHITE (INCLUDING HISPANIC WHITES), 0 = OTHERWISE
    black, # 1 = R IS BLACK NON-HISPANIC, 0 = OTHERWISE
    asian, # 1 = R IS ASIAN NON-HISPANIC, 0 = OTHERWISE
    natamer, # 1 = R IS NATIVE AMERICAN NON-HISPANIC, 0 = OTHERWISE
    otherrace, # 1 = R IS OTHER OR MIXED RACE, 0 = OTHERWISE
    gender, # 1 = R IS A WOMAN, 0 = MAN
    govservice, # GOV SERVICES SCALE: 6 = GOV SHOULD PROVIDE MORE SERVICES
    medinsur, # MEDICAL INSURANCE SCALE: 6 = GOV INSUANCE ... 0 = PRIVATE INSURANCE
    fedgun, # 2 = GUN PURCHASE EASIER, 1 = THE SAME, 0 = GUN PURCHASE MORE DIFFICULT
    govjob, # GOV JOB SCALE: 6 = GOV GUARANTEES JOBS ... 0 = GET JOBS ON OWN
    govblacks, # AID TO BLACKS SCALE: 6 = GOV SHOULD HELP BLACKS ... 0 = BLACKS HELP SELVES
    ssocsec, # 1 = INCREASED SPENDING ON SOCSEC, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sschools, # 1 = INCREASED SPENDING ON SCHOOLS, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sscience, # 1 = INCREASED SPENDING ON SCIENCE, 0 = KEEP SAME, -1 DECREASED SPENDING
    swelfare, # 1 = INCREASED SPENDING ON WELFARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    schildcare, # 1 = INCREASED SPEND ON CHILD CARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    spoor, # 1 = INCREASED SPEND ON POOR, 0 = KEEP SAME, -1 = DECREASED SPENDING
    senviron, # 1 = INCREASED SPEND ON ENVIRONMENT, 0 = KEEP SAME, -1 = DECREASED,
    gwaction, # 6 = GOV SHOULD BE DOING GREAT DEAL MORE FOR GLOBAL WARMING ... 0 = LESS
    govinequality, # 2 = R SUPPORT GOV EFFORTS TO REDUCE INEQUALITY, 1 = NEUTRAL, 0 = OPPOSE
    shealthcare7, # 6 = SUPPORT STRONG INCREASE IN HEALTH CARE SPEND, 0 = STRONG DECREASE
    taxmillion, # 2 = SUPPORTS INCREASING TAXES ON MILLIONAIRES, 1 = NEUTRAL, 0 = OPPOSE
    govprob, # 1 = GOV DOING TOO MUCH, 0 = PROBLEMS ARE BIGGER
    fmarket, # 1 = FREE MARKET CAN HANDLE PROBLEMS, 0 = GOV NEEDED TO SOLVE PROBLEMS
    govless, # 1 = LESS GOV THE BETTER, 0 = GOV SHOULD DO MORE THINGS
    gregbus, # 4 = A GREAT DEAL OF REGULATION IS GOOD FOR SOCIETY ... 0 = NONE AT ALL
  ))

# remove NA
econ2016 <- na.omit(econ2016)

# reverse code so high values indicate more liberal issue positions
econ2016 <- econ2016 %>%
  mutate(libcon = recode(libcon, #recode so 6 = strong liberal and 0 = strong conservative
                         `0` = 6,
                         `1` = 5,
                         `2` = 4, 
                         `4` = 2,
                         `5` = 1, 
                         `6` = 0
                          )) %>%
  mutate(partyid = recode(partyid, #recode so 6 = strong Democrat and 0 = strong Republican
                          `0` = 6,
                          `1` = 5,
                          `2` = 4, 
                          `4` = 2,
                          `5` = 1, 
                          `6` = 0
                          ))  %>%
  mutate(fedgun = recode(fedgun, #recode so 2 = gun purchase more difficult and 0 = gun purchase more easy
                         `0` = 2,
                         `2` = 0
                          )) %>%
  mutate(ssocsec = recode(ssocsec, #recode so 2 = more spending, 1 = stay the same, 0 = decrease spending
                          `1` = 2,
                          `0` = 1,
                          `-1` = 0
                          )) %>%
  mutate(sschools = recode(sschools, #recode so 2 = increased spending, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(sscience = recode(sscience, #recode 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(swelfare = recode(swelfare, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(schildcare = recode(schildcare, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(spoor = recode(spoor, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(senviron = recode(senviron, #reverse code 2 = increased spend, 1 = stay the same, 0 = decrease
                           `1` = 2,
                           `0` = 1,
                           `-1` = 0
                           )) %>%
  mutate(govprob = recode(govprob, #reverse code 1 = problems are bigger, 0 = gov doing too much
                          `1` = 0,
                          `0` = 1
                          )) %>%
  mutate(fmarket = recode(fmarket, #reverse code 1 = gov needed to solve problems, 0 = free market can handle
                          `1` = 0,
                          `0` = 1
                          )) %>%
  mutate(govless = recode(govless, #reverse code 1 = gov should do more things, 0 = less gov the better
                          `1` = 0,
                          `0` = 1
                          ))
  
#create factor score by dividing each column by the number of questions to give a value between 0 and 1
econ2016 <- econ2016 %>%
  mutate(govservice1 = govservice / 6) %>%
  mutate(medinsur1 = medinsur / 6) %>%
  mutate(fedgun1 = fedgun / 2) %>%
  mutate(govjob1 = govjob / 6) %>%
  mutate(govblacks1 = govblacks / 6) %>%
  mutate(ssocsec1 = ssocsec / 2) %>%
  mutate(sschools1 = sschools / 2) %>%
  mutate(sscience1 = sscience / 2) %>%
  mutate(swelfare1 = swelfare / 2) %>%
  mutate(schildcare1 = schildcare / 2) %>%
  mutate(spoor1 = spoor / 2) %>%
  mutate(senviron1 = senviron / 2) %>%
  mutate(gwaction1 = gwaction / 6) %>%
  mutate(govinequality1 = govinequality / 2) %>%
  mutate(shealthcare71 = shealthcare7 / 6) %>%
  mutate(taxmillion1 = taxmillion / 2) %>%
  mutate(govprob1 = govprob / 1) %>%
  mutate(fmarket1 = fmarket / 1) %>%
  mutate(govless1 = govless / 1) %>%
  mutate(gregbus1 = gregbus / 4)

#add all together to create single factor score for economic dimension
 econ2016 <- econ2016 %>%
  dplyr::mutate(fecon2016 = 
           govservice1 + 
           medinsur1 + 
           govjob1 + 
           ssocsec1 +
           sschools1 +
           sscience1 +
           swelfare1 +
           schildcare1 +
           spoor1 +
           senviron1
           )

# check range of factor score to be 0 (most conservative) to 10 (most liberal)
range(econ2016$fecon2016)

# select needed variables
econ2016 <- econ2016 %>%
  select("caseid", "stfips", "stabbrev", "congdist", "libcon", "partyid", "educ", "race", "hispanic", "white", "white1", "black", "asian", "natamer", "otherrace", "gender", "fecon2016")
```

## Population Density from ArcGIS Hub
[Source](https://hub.arcgis.com/datasets/ff48bbae433442a38f6c635b8c7baf72_0/data?geometry=11.844%2C-0.129%2C102.899%2C76.650)
```{r}
# create data frame
geo2016 <- geo %>%
  select(c(
    OBJECTID,
    ID,
    NAME, # NAME OF THE CONGRESSIONAL DISTRICT
    ST_ABBREV,
    TOTPOP_CY, # TOTAL POPULATION OF DISTRICT IN 2016
    POPDENS_CY, # POPULATION DENSITY OF DISTRICT IN 2016
    POPGRW10CY # POPULATION GROWTH RATE 2010 - 2016
  ))

# remove alphabetic characters to give only district number
geo2016$NAME <- gsub("[a-zA-Z ]", "", geo2016$NAME)

# remove dash in district number
geo2016$NAME <- gsub("\\-", "", geo2016$NAME)

# make district number vector numeric
 geo2016$NAME <- as.double(geo2016$NAME)

# add leading zeros to district number
geo2016$NAME <- sprintf("%02d", geo2016$NAME)

# turn ST_ABBREV into a character variable
geo2016$ST_ABBREV <- as.character(geo2016$ST_ABBREV)

# combine ST_ABBREV and NAME to form CD (consistent with other data set)
geo2016 <- geo2016 %>%
  unite(col = "CD", ST_ABBREV:NAME, sep = "-")

# make CD a character variable
geo2016$CD <- as.character(geo2016$CD)

# turn POPDENS_CY into a numeric
geo2016$POPDENS_CY <- as.numeric(geo2016$POPDENS_CY)

# round to whole numbers
#geo2016$POPDENS_CY <- round(geo2016$POPDENS_CY, digits = 0)

# rename columns to be compatible with other data frames
#geo2016recoded <- geo2016recoded %>%
#  rename(
#    stabbrev = ST_ABBREV,
#    congdist = NAME
#  )


```

## Daily Kos Election Results
```{r}
dailykos <- read_csv("Daily Kos Elections 2008, 2012 & 2016 presidential election results for congressional districts used in 2016 elections - Results.csv", 
                     skip = 1)

# make variable for % Clinton vote into blue vote
election <- dailykos %>%
  mutate(bluevote = Clinton)

# select needed variables
election <- election %>%
  select("CD", "bluevote")
```

# Combine Data Sets

## Daily Kos + ArcGIS
```{r}
# combine data sets using CD variable -- same format
combine2016 <- merge(geo2016, election, by = c("CD"))
```

## Add ANES data
```{r}
# alter formatting of CD variable to be like ANES
combine2016 <- combine2016 %>%
  separate("CD", (c("stabbrev", "congdist0")), sep = "-")

# add leading 0 into ANES
econ2016$congdist0 <- str_pad(econ2016$congdist, width = 2, side = "left", pad = "0")

# combine two data sets
combine2016 <- merge(econ2016, combine2016, by = c("stabbrev", "congdist0"))
```

# Distributions of Variables

## Education
1 = less than high school
2 = high school, no diploma
3 = high school diploma or equivalent
4 = some college, no degree
5 = Associate degree
6 = Bachelor's degree
7 = Master's degree
8 = Doctorate or Professional degree
```{r}
summary(combine2016$educ)
```
* Sample leans toward high school educated and some college
```{r}
ggplot(combine2016, aes(x = educ)) +
  geom_bar() +
  xlab("Respondent Education") +
  ylab("Number of Respondents")
```

## Race
1 = WHITE
2 = BLACK
3 = ASIAN
4 = NATIVE
5 = HISPANIC
6 = OTHER
```{r}
summary(combine2016$race)
```
* Majority of respondents are white
```{r}
ggplot(combine2016, aes(x = race)) +
  geom_bar()
```

## Gender
1 = Woman
0 = Man
```{r}
summary(combine2016$gender)
```
* Respondents are about equal male and female
```{r}
ggplot(combine2016, aes(x = gender)) +
  geom_bar()
```


## Economic issue positions
```{r}
summary(combine2016$fecon2016)
```
* Sample issue positions lean liberal
```{r}
hist(combine2016$fecon2016)
```

## Liberal/Conservative
```{r}
summary(combine2016$libcon)
```
* sample identity leans conservative
```{r}
ggplot(combine2016, aes(x = libcon)) +
  geom_bar()
```

## Party ID
```{r}
summary(combine2016$partyid)
```
* Sample party ID is clustered at the extremes
```{r}
ggplot(econ2016, aes(x = partyid)) +
  geom_bar()
```

## Population Density
```{r}
summary(combine2016$POPDENS_CY)
```
* Population density is unevenly distributed -- most in the lower numbers
```{r}
hist(combine2016$POPDENS_CY)
```

## District voting
```{r}
summary(combine2016$bluevote)
```
* District voting skews Red (predicted because of election outcome)
```{r}
hist(combine2016$bluevote)
```


# Group Respondents by Identification
```{r}
# Political ID
all_lib <- filter(combine2016, libcon == c(6, 5, 4)) # ALL LIBERAL

st_lib <- filter(combine2016, libcon == 6) # STRONG LIBERAL

lib <- filter(combine2016, libcon == 5) # LIBERAL

m_lib <- filter(combine2016, libcon == 4) # MODERATE LIBERAL

mod_id <- filter(combine2016, libcon == 3) # MODERATE

m_con <- filter(combine2016, libcon == 2) # MODERATE CONSERVATIVE

con <- filter(combine2016, libcon == 1) # CONSERVATIVE

st_con <- filter(combine2016, libcon == 0) # STRONG CONSERVATIVE

all_con <- filter(combine2016, libcon == c(2, 1, 0)) # ALL CONSERVATIVE

# Party ID
all_dem <- filter(combine2016, partyid == c(6, 5, 4)) # ALL DEMOCRAT

st_dem <- filter(combine2016, partyid == 6) # STRONG DEMOCRAT

dem <- filter(combine2016, partyid == 5) # DEMOCRAT

m_dem <- filter(combine2016, partyid == 4) # MODERATE DEMOCRAT

mod_party <- filter(combine2016, partyid == 3) # MODERATE

m_rep <- filter(combine2016, partyid == 2) # MODERATE REPUBLICAN

rep <- filter(combine2016, partyid == 1) # REPUBLICAN

st_rep <- filter(combine2016, partyid == 0) # STRONG REPUBLICAN

all_rep <- filter(combine2016, partyid == c(0, 1, 2)) # ALL REPUBLICAN
```

## Look at distribution for each group

Strong Liberals
```{r}
summary(st_lib$fecon2016)
```
* Issue positions lean strongly liberal - no conflicted
```{r}
hist(st_lib$fecon2016)
```
* pop dens pretty rural but some urban
```{r}
hist(st_lib$POPDENS_CY, breaks = 300)
hist(st_lib$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more blue
```{r}
hist(st_lib$bluevote)
```


Liberals
```{r}
summary(lib$fecon2016)
```
* Issue positions lean pretty liberalm - few conflicted
```{r}
hist(lib$fecon2016)
```
* pop dens pretty rural with some urban
```{r}
hist(lib$POPDENS_CY, breaks = 300)
hist(lib$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more blue
```{r}
hist(lib$bluevote)
```


Moderate Liberals
```{r}
summary(m_lib$fecon2016)
```
* Issue positions lean liberal - some conflicted
```{r}
hist(m_lib$fecon2016)
```
* pop dens pretty rural with some urban
```{r}
hist(m_lib$POPDENS_CY, breaks = 300)
hist(m_lib$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more center
```{r}
hist(m_lib$bluevote)
```


Moderates
```{r}
summary(mod_id$fecon2016)
```
* Issue positions still lean pretty liberal
```{r}
hist(mod_party$fecon2016)
```
* pop dens pretty rural with few urban
```{r}
hist(mod_party$POPDENS_CY, breaks = 300)
hist(mod_party$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(mod_party$bluevote)
```



Moderate Conservatives
```{r}
summary(m_con$fecon2016)
```
* Issue positions clustered in the middle - some conflicted
```{r}
hist(m_con$fecon2016)
```
* pop dens pretty rural very few urban
```{r}
hist(m_con$POPDENS_CY, breaks = 300)
hist(m_con$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(m_con$bluevote)
```


Conservatives
```{r}
summary(con$fecon2016)
```
* Issue positions lean conservative -- some conflicted
```{r}
hist(con$fecon2016)
```
* pop dens pretty rural with very few urban
```{r}
hist(con$POPDENS_CY, breaks = 300)
hist(con$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(con$bluevote)
```


Strong Conservatives
```{r}
summary(st_con$fecon2016)
```
* Issue positions lean conservative - some conflicted
```{r}
hist(st_con$fecon2016)
```
* pop dens pretty rural
```{r}
hist(st_con$POPDENS_CY, breaks = 300)
hist(st_con$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(st_con$bluevote)
```



Strong Democrats
```{r}
summary(st_dem$fecon2016)
```
* Issue positions lean pretty liberal - some conflicted
```{r}
hist(st_dem$fecon2016)
```
* pop dens rural with some urban
```{r}
hist(st_dem$POPDENS_CY, breaks = 300)
hist(st_dem$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(st_dem$bluevote)
```



Democrat
```{r}
summary(dem$fecon2016)
```
* Issue positions lean pretty liberal - some conflicted
```{r}
hist(dem$fecon2016)
```
* pop dens pretty rural
```{r}
hist(dem$POPDENS_CY, breaks = 300)
hist(dem$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context diverse
```{r}
hist(dem$bluevote)
```



Moderate Democrats
```{r}
summary(m_dem$fecon2016)
```
* Issue positions lean pretty liberal - some conflicted
```{r}
hist(m_dem$fecon2016)
```
* pop dens pretty rural
```{r}
hist(m_dem$POPDENS_CY, breaks = 300)
hist(m_dem$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context all over
```{r}
hist(m_dem$bluevote)
```




Moderate Party
```{r}
summary(mod_party$fecon2016)
```
* Issue positions lean pretty liberal
```{r}
hist(mod_party$fecon2016)
```
* pop dens pretty rural
```{r}
hist(mod_party$POPDENS_CY, breaks = 300)
hist(mod_party$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(mod_party$bluevote)
```


Moderate Republican
```{r}
summary(m_rep$fecon2016)
```
* Issue positions lean pretty central - some conflicted
```{r}
hist(m_rep$fecon2016)
```
* pop dens pretty rural
```{r}
hist(m_rep$POPDENS_CY, breaks = 300)
hist(m_rep$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(m_rep$bluevote)
```



Republican
```{r}
summary(rep$fecon2016)
```
* Issue positions lean pretty center - some conflicted
```{r}
hist(rep$fecon2016)
```
* pop dens pretty rural
```{r}
hist(rep$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* pop dens pretty rural
```{r}
hist(rep$POPDENS_CY, breaks = 300)
hist(rep$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(rep$bluevote)
```


Strong Republican
```{r}
summary(st_rep$fecon2016)
```
* Issue positions pretty center - some conflicted
```{r}
hist(st_rep$fecon2016)
```
* pop dens pretty rural
```{r}
hist(st_rep$POPDENS_CY, breaks = 300)
hist(st_rep$POPDENS_CY, breaks = 300, xlim = c(10, 2500))
```
* voting context leans more red
```{r}
hist(st_rep$bluevote)
```



