---
title: "Consolidate1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(haven)
library(gmodels)
```

# Import Data Sets

## ANES
```{r}
anes2016all <- read_dta("anes2016.dta")
```

## City Lab
Taken from [City Lab](https://github.com/theatlantic/citylab-data/tree/master/citylab-congress)
citylab_cdi_extended.csv
```{r}
citylab <- read_csv("citylab_cdi.csv")
```

## Daily Kos
```{r}
dailykos <- read_csv("Daily Kos Elections 2008, 2012 & 2016 presidential election results for congressional districts used in 2016 elections - Results.csv", 
                     skip = 1)
```


# Select and Recode Needed Variables

## ANES economic data **still need to figure out what to do about social class variable**
```{r}
# select needed economic variables
econ2016 <- anes2016all %>%
  select(c(
    caseid,
    stfips, # STATE FIPS CODE
    stabbrev, # STATE ABBREVIATION
    congdist, # CONGRESSIONAL DISTRICT NUMBER
    libcon, # POLITICAL ID (FORCED): 6 = STRONG CONSERVATIVE ... 0 = STRONG LIBERAL
    partyid, # PARTISAN ID: 6 = STRONG REP ... 0 = STRONG DEM
    V161267x, # PRE: SUMMARY - RESPONDENT AGE GROUP
    educ, # 1 = LESS THAN HIGH SCHOOL ... 8 = DOCTORATE OR PROFESSIONAL
    V161270, # PRE: HIGHEST LEVEL OF EDUCATION
    race, # 1 = WHITE, 2 = BLACK, 3 = ASIAN, 4 = NATIVE, 5 = HISPANIC, 6 = OTHER
    hispanic, # 1 = R IS HISPANIC, 0 = OTHERWISE
    white, # 1 = R IS WHITE NON-HISPANIC, 0 = OTHERWISE
    white1, # 1 = R IS WHITE (INCLUDING HISPANIC WHITES), 0 = OTHERWISE
    black, # 1 = R IS BLACK NON-HISPANIC, 0 = OTHERWISE
    asian, # 1 = R IS ASIAN NON-HISPANIC, 0 = OTHERWISE
    natamer, # 1 = R IS NATIVE AMERICAN NON-HISPANIC, 0 = OTHERWISE
    otherrace, # 1 = R IS OTHER OR MIXED RACE, 0 = OTHERWISE
    gender, # 1 = R IS A WOMAN, 0 = MAN
    govservice, # GOV SERVICES SCALE: 6 = GOV SHOULD PROVIDE MORE SERVICES
    medinsur, # MEDICAL INSURANCE SCALE: 6 = GOV INSUANCE ... 0 = PRIVATE INSURANCE
    fedgun, # 2 = GUN PURCHASE EASIER, 1 = THE SAME, 0 = GUN PURCHASE MORE DIFFICULT
    govjob, # GOV JOB SCALE: 6 = GOV GUARANTEES JOBS ... 0 = GET JOBS ON OWN
    govblacks, # AID TO BLACKS SCALE: 6 = GOV SHOULD HELP BLACKS ... 0 = BLACKS HELP SELVES
    ssocsec, # 1 = INCREASED SPENDING ON SOCSEC, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sschools, # 1 = INCREASED SPENDING ON SCHOOLS, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sscience, # 1 = INCREASED SPENDING ON SCIENCE, 0 = KEEP SAME, -1 DECREASED SPENDING
    swelfare, # 1 = INCREASED SPENDING ON WELFARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    schildcare, # 1 = INCREASED SPEND ON CHILD CARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    spoor, # 1 = INCREASED SPEND ON POOR, 0 = KEEP SAME, -1 = DECREASED SPENDING
    senviron, # 1 = INCREASED SPEND ON ENVIRONMENT, 0 = KEEP SAME, -1 = DECREASED,
    gwaction, # 6 = GOV SHOULD BE DOING GREAT DEAL MORE FOR GLOBAL WARMING ... 0 = LESS
    govinequality, # 2 = R SUPPORT GOV EFFORTS TO REDUCE INEQUALITY, 1 = NEUTRAL, 0 = OPPOSE
    shealthcare7, # 6 = SUPPORT STRONG INCREASE IN HEALTH CARE SPEND, 0 = STRONG DECREASE
    taxmillion, # 2 = SUPPORTS INCREASING TAXES ON MILLIONAIRES, 1 = NEUTRAL, 0 = OPPOSE
    govprob, # 1 = GOV DOING TOO MUCH, 0 = PROBLEMS ARE BIGGER
    fmarket, # 1 = FREE MARKET CAN HANDLE PROBLEMS, 0 = GOV NEEDED TO SOLVE PROBLEMS
    govless, # 1 = LESS GOV THE BETTER, 0 = GOV SHOULD DO MORE THINGS
    gregbus, # 4 = A GREAT DEAL OF REGULATION IS GOOD FOR SOCIETY ... 0 = NONE AT ALL
  ))

# remove NA
econ2016 <- na.omit(econ2016)

# ensure larger numbers are always liberal
econ2016 <- econ2016 %>%
  mutate(libcon = recode(libcon, #recode so 6 = strong liberal and 0 = strong conservative
                         `0` = 6,
                         `1` = 5,
                         `2` = 4, 
                         `4` = 2,
                         `5` = 1, 
                         `6` = 0
                          )) %>%
  mutate(partyid = recode(partyid, #recode so 6 = strong Democrat and 0 = strong Republican
                          `0` = 6,
                          `1` = 5,
                          `2` = 4, 
                          `4` = 2,
                          `5` = 1, 
                          `6` = 0
                          )) # %>%
#  mutate(educ5 = recode(V161270, # recode to fewer categories
#                       `1` = 0, # (was less than 1st) 0 = less than high school diploma
#                       `2` = 0, # (was 1st - 4th) 0 = less than high school diploma
#                       `3` = 0, # (was 5 - 6) 0 = less than high school diploma
#                       `4` = 0, # (was 7-8) 0 = less than high school diploma
#                       `5` = 0, # (was 9) 0 = less than high school diploma
#                       `6` = 0, # (was 10) 0 = less than high school diploma
#                       `7` = 0, # (was 11) 0 = less than high school diploma
#                       `8` = 0, # (was 12) 0 = less than high school diploma
#                       `9` = 1, # 1 = high school diploma or equivalency
#                       `10` = 2, # 2 = some college but no degree
#                       `11` = 3, # 3 = Associate degree
#                       `12` = 3, # 3 = Associate degree
#                       `13` = 4, # 4 = Bachelor's degree or higher
#                       `14` = 4, # 4 = Bachelor's degree or higher
#                       `15` = 4, # 4 = Bachelor's degree or higher
#                       `16` = 4, # 4 = Bachelor's degree or higher
#                       `90` = 1, # 1 = high school diploma
#                       `95` = 9, # 9 = other or refused
#                       `9` = 9 # 9 = other or refused
#                       ))

# collapse larger scales
econ2016 <- econ2016 %>%
  mutate(govservice1 = recode(govservice,
                              `6` = 1,
                              `5` = 1,
                              `4` = 1,
                              `3` = 0, 
                              `2` = -1,
                              `1` = -1, 
                              `0` = -1
                              )) %>%
  mutate(medinsur1 = recode(medinsur,
                            `6` = 1,
                            `5` = 1,
                            `4` = 1,
                            `3` = 0, 
                            `2` = -1,
                            `1` = -1, 
                            `0` = -1
                            )) %>%
  mutate(govjob1 = recode(govjob,
                          `6` = 1,
                          `5` = 1,
                          `4` = 1,
                          `3` = 0, 
                          `2` = -1,
                          `1` = -1, 
                          `0` = -1))

# create additive scale of all econ answers
econ2016 <- econ2016 %>%
  mutate(fecon2016 = 
           govservice1 + 
           medinsur1 + 
           govjob1 + 
           ssocsec +
           sschools +
           sscience +
           swelfare +
           schildcare +
           spoor +
           senviron)

# select needed variables
econ2016 <- econ2016 %>%
  select("caseid", "stfips", "stabbrev", "congdist", "libcon", "partyid", "educ", "race", "hispanic", "white", "white1", "black", "asian", "natamer", "otherrace", "gender", "fecon2016")
```

## City Lab Urban/Rural Classification
```{r}
# Recode Cluster to be categorical numeric of decreasing urbanity/increasing rural
districtpop <- citylab %>%
  mutate(clust = ifelse(Cluster == "Pure rural", 6,
                        ifelse(Cluster == "Rural-suburban mix", 5,
                               ifelse(Cluster == "Sparse suburban", 4,
                                      ifelse(Cluster == "Dense suburban", 3,
                                             ifelse(Cluster == "Urban-suburban mix", 2,
                                                    ifelse(Cluster == "Pure urban", 1, 0
                                                           )))))))

#select needed variables
districtpop <- districtpop %>%
  select("CD", "clust", "Cluster")
```

## Daily Kos percent voted blue
```{r}
# make variable for % Clinton vote into blue vote
election <- dailykos %>%
  mutate(bluevote = Clinton)

# select needed variables
election <- election %>%
  select("CD", "bluevote")
```


# Combine Data Sets

## Daily Kos + City Lab 
```{r}
# combine data sets using CD variable -- same format
combine2016 <- merge(districtpop, election, by = c("CD"))
```

## Add ANES data
```{r}
# alter formatting of CD variable to be like ANES
combine2016 <- combine2016 %>%
  separate("CD", (c("stabbrev", "congdist0")), sep = "-")

# add leading 0 into ANES
econ2016$congdist0 <- str_pad(econ2016$congdist, width = 2, side = "left", pad = "0")

# combine two data sets
combine2016 <- merge(econ2016, combine2016, by = c("stabbrev", "congdist0"))
```


# Distributions of Variables

## Economic issue positions
```{r}
hist(econ2016$fecon2016)
```

## Liberal/Conservative
```{r}
hist(econ2016$libcon)
```

## Party ID
```{r}
hist(econ2016$partyid)
```

# Cross Tabulations

## Issue positions and ideological identification
```{r}
CrossTable(combine2016$fecon2016, combine2016$libcon)
```


# Regressions

Multiple Linear Regression Example:
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results

## Model 1: Urban/rural (x = clust) effects policy positions (y)
```{r}
first <- lm(fecon2016 ~ clust, data = combine2016)
summary(first)
```
```{r}
# create new dataframes for each political ID
alllib <- filter(combine2016, libcon == c(6, 5, 4))

stlib <- filter(combine2016, libcon == 6) # STRONG LIBERAL

lib <- filter(combine2016, libcon == 5) # LIBERAL

mlib <- filter(combine2016, libcon == 4) # MODERATE LIBERAL

mod <- filter(combine2016, libcon == 3) # MODERATE

mcon <- filter(combine2016, libcon == 2) # MODERATE CONSERVATIVE

con <- filter(combine2016, libcon == 1) # CONSERVATIVE

scon <- filter(combine2016, libcon == 0) # STRONG CONSERVATIVE

allcon <- filter(combine2016, libcon == c(2, 1, 0))

# create new dataframes for party ID
sdem <- filter(combine2016, partyid == 6) # STRONG DEMOCRAT

srep <- filter(combine2016, partyid == 0) # STRONG REPUBLICAN

# create new dataframes for each urban/rural classification

```




## Model 2: Urban/rural + district blueness effect on issue positions
```{r}
second <- lm(fecon2016 ~ clust + bluevote, data = combine2016)
summary(second)
```




