---
title: "Cultural Dimension"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
```

# Cultural Dimension

Ellis and Stimson (2012) find what they call the "economic" and "cultural dimensions" of public policy preferences to have a statistically negligable difference.
**Use Cramer's work to justify why looking at cultural**

## Criterion variables for interpreting the cultural dimension

* Capital punishment
* Homosexual marriage
* Immigration
* Homosexual job rights
* Birth control 
* Privacy

**add in vaccines, just because it's interesting**

```{r}
cultural2016 <- anes2016recode %>%
  select(c(
    caseid,
    libcon, # POLITICAL ID (FORCED): 6 = STRONG CONSERVATIVE ... 0 = STRONG LIBERAL
    partyid, # PARTISAN ID: 6 = STRONG REP ... 0 = STRONG DEM
    immpolicy, # 3 = REMAIN NO PENALTY, 2 = REMAIN PENALTY, 1 = GUEST WORKER, 0 = DEPORT
    immnopenalty, # 1 = REMAIN IN US WITHOUT PENALTY, 0 = OTHERWISE
    immpenalty, # 1 = REMAIN IN US BUT WITH PENALTY, 0 = OTHERWISE
    immguest, # 1 = REMAIN IN US GUEST WORKER PROGRAM, 0 = OTHERWISE
    immdeport, # 1 = ILLEGAL IMMIGRANTS CLASSIFIED AS FELONS AND DEPORTED, 0 = OTHERWISE
    immbirth, # 6 = R SUPPORTS BIRTHRIGHT CITIZENSHIP ... 0 = R SUPPORTS BIRTHPLACE CITIZENS
    immcitizen, # 5 = R SUPPORTS SENDING IMMIGRANT CHILDREN BACK ... 0 = ALLOWED TO STAY
    aacolleges, # 6 = R SUPPORTS AFFIRMATIVE ACTION IN COLLEGES ... 0 = R OPPOSES
    glservice, # 5 = REQUIRE SERVICE FOR GAY COUPLES ... 0 = REFUSE SERVICE
    transbath, # 5 = TRANS USE BATHROOM OF CHOICE ... 0 = USE BATHROOM OF GENDER BORN WITH
    gaydiscrim, # 3 = STRONGLY FAVOR ANTIDISCRIMINATION LAWS ... 0 = STRONGLY OPPOSE
    gayadopt, # 1 = GAYS AND LESBIANS SHOULD BE ABLE TO ADOPT CHILDREN, 0 = SHOULD NOT
    abortion, # 3 = ALL CIRCUMSTANCE, 2 = MANY REASONS, 1 = RAPE, ETC., 0 = NEVER
    dpenalty, # 3 = STRONGLY SUPPORTS DEATH PENALTY ... 0 = STRONGLY OPPOSES
    vaccines, # 6 = STRONGLY SUPPORTS VACCINES IN SCHOOLS ... 0 = STRONGLY OPPOSE
    pubsecurity, # 2 = CHANGES IN SECURITY GONE TOO FAR, 1 = ABOUT RIGHT, 0 = NOT FAR ENOUGH
    immlevel, # 4 = IMMIGRATION SHOULD BE INCREASED A LOT ... 0 = DECREASED A LOT
    benriskvaccines, # 6 = BENEFITS MUCH GREATER FOR VACCINES ... 0 = RISK MUCH GREATER
    govwiretaps, # 2 = GOV WIRETAPS GONE TOO FAR, 1 = ABOUT RIGHT, 0 = NOT FAR ENOUGH
    gaymarriage, # 1 = GAYS AND LESBIANS CAN MARRY, 0 = CIVIL UNIONS, -1 = NO LEGAL RECOG
  ))
```

