---
title: "Geographic Data"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

Data from ArcGIS Hub

[here](https://hub.arcgis.com/datasets/ff48bbae433442a38f6c635b8c7baf72_0/data?geometry=11.844%2C-0.129%2C102.899%2C76.650)

Filter data set for selected variables

* ObjectID
* ID
* Name
* State Abbreviation
* 2016 Total Population
* 2016 Population Density (Pop per square mile)
* 2010 - 2016 Population: Annual Growth Rate

```{r}
geo2016 <- geo %>%
  select(c(
    OBJECTID,
    ID,
    NAME, # NAME OF THE CONGRESSIONAL DISTRICT
    ST_ABBREV,
    TOTPOP_CY, # TOTAL POPULATION OF DISTRICT IN 2016
    POPDENS_CY, # POPULATION DENSITY OF DISTRICT IN 2016
    POPGRW10CY # POPULATION GROWTH RATE 2010 - 2016
  ))
```

Remove characters from NAME to leave just the congressional district number

```{r}
geo2016recoded <- geo2016

# remove alphabetic characters
geo2016recoded$NAME <- gsub("[a-zA-Z ]", "", geo2016$NAME)

# remove dash
geo2016recoded$NAME <- gsub("\\-", "", geo2016recoded$NAME)

# make vector numeric
geo2016recoded$NAME <- as.double(geo2016recoded$NAME)

# turn ST_ABBREV into a character variable
geo2016recoded$ST_ABBREV <- as.character(geo2016recoded$ST_ABBREV)

# turn POPDENS_CY into a numeric
geo2016recoded$POPDENS_CY <- as.numeric(geo2016recoded$POPDENS_CY)

# round to whole numbers
geo2016recoded$POPDENS_CY <- round(geo2016recoded$POPDENS_CY, digits = 0)
```

Rename columns to be equivalent with that of columns from economic

```{r}
geo2016recoded <- geo2016recoded %>%
  rename(
    stabbrev = ST_ABBREV,
    congdist = NAME
  )
```





Don't use: Make Population Density into a categorical variable
```{r}
#geo2016recoded <- geo2016recoded %>%
##  mutate(popdens = ifelse(POPDENS_CY %in% 0:49, 1, 
#   ifelse(POPDENS_CY %in% 50:99, 50,
#    ifelse(POPDENS_CY %in% 100:149, 100,
#      ifelse(POPDENS_CY %in% 150:199, 150,
#       ifelse(POPDENS_CY %in% 200:249, 200,
#        ifelse(POPDENS_CY %in% 250:299, 250,
#         ifelse(POPDENS_CY %in% 300:349, 300,
#          ifelse(POPDENS_CY %in% 350:399, 350,
#           ifelse(POPDENS_CY %in% 400:449, 400,
#            ifelse(POPDENS_CY %in% 450:499, 450,
#             ifelse(POPDENS_CY %in% 500:549, 500,
#              ifelse(POPDENS_CY %in% 550:599, 550,
#               ifelse(POPDENS_CY %in% 600:649, 600,
 #               ifelse(POPDENS_CY %in% 650:699, 650,
#                 ifelse(POPDENS_CY %in% 700:749, 700,
#                  ifelse(POPDENS_CY %in% 750:799, 750,
#                   ifelse(POPDENS_CY %in% 800:849, 800,
#                    ifelse(POPDENS_CY %in% 850:899, 850,
##                     ifelse(POPDENS_CY %in% 900:949, 900,
#                      ifelse(POPDENS_CY %in% 950:999, 950,
#                       ifelse(POPDENS_CY %in% 1000:1049, 1000,
#                        ifelse(POPDENS_CY %in% 1050:1099, 1050,
#                         ifelse(POPDENS_CY %in% 1100:1149, 1100,
#                          ifelse(POPDENS_CY %in% 1150:1199, 1150,
#                           ifelse(POPDENS_CY %in% 1200:1249, 1200,
#                            ifelse(POPDENS_CY %in% 1250:1299, 1250,
#                             ifelse(POPDENS_CY %in% 1300:1349, 1300,
#                              ifelse(POPDENS_CY %in% 1350:1399, 1350,
#                               ifelse(POPDENS_CY %in% 1400:1459, 1400, 999999
#                              ))))))))))))))))))))))))))))))

# need to figure out how to distribute the population better
# maybe you just need to remove the outliers at the very end, maybe anything over 4,000 per square mile?
```

```{r}
hist(geo2016recoded$popdens)
```

