---
title: "Model 1 Regress with Continuous Variables"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(haven)
library(gmodels)
library(survey)
library(jtools)
options("jtools-digits" = 8)
```

# Notes



Multiple Linear Regression Example:
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results

## Model 1: Urban/rural (x = POPDENS_CY) effects policy positions (y = fecon2016) for each of the ideological and party identities

*demographic variables: "hispanic" "white", "white1", "black", "asian", "natamer", "otherrace", "gender", "fecon2016", "age18_24", "age25_34", "age35_44", "age45_54", "age55_64", "age65_74", "age75", "lessdiploma", "somecoll", "associate", "bachelors", "grad"



Overall
```{r}

d_design <- svydesign(ids = ~1, weights = ~weight, data = combine2016)

#summ()
  
overall1  <- svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = d_design)

summ(overall1)

#regress1_stlib <- lm(fecon2016 ~  POPDENS_CY + factor(race) + gender + factor(educ), data = st_lib)
                     
  # + hispanic + black + asian + natamer + otherrace + gender + age25_34 + age35_44 + age45_54 + age55_64 + age65_74 + age75 + somecoll + associate + bachelors + grad, data = st_lib)
```
Condensed Liberal
```{r}
alllib_design <- svydesign(ids = ~1, weights = ~weight, data = all_lib)

alllib1 <- svyglm(formula = fecon2016 ~ POPDENS_CY, design = alllib_design)
summ(alllib1)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = alllib_design))
```

Strong Liberal
```{r}
stlib_design <- svydesign(ids = ~1, weights = ~weight, data = st_lib)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = stlib_design))
```
* The econ factor score is predicted to increase (become more liberal) 1.058e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the factor score is at 
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.147, so it is not significant

Liberal
```{r}
#regress1_lib <- lm(fecon2016 ~ POPDENS_CY, data = lib)
#summary(regress1_lib)

lib_design <- svydesign(ids = ~1, weights = ~weight, data = lib)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = lib_design))
```
* The econ factor score is predicted to increase (become more liberal) 1.436e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 9.498
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0564, so it is significant at p<0.1

Moderate Liberal
```{r}
#regress1_mlib <- lm(fecon2016 ~ POPDENS_CY, data = m_lib)
#summary(regress1_mlib)

mlib1_design <- svydesign(ids = ~1, weights = ~weight, data = m_lib)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = mlib1_design))
```
* The econ factor score is predicted to increase (become more liberal) 2.86e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.866
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0105, so it is significant at p<0.05

Moderate Ideology
```{r}
#regress1_modid <- lm(fecon2016 ~ POPDENS_CY, data = mod_id)
#summary(regress1_modid)

modid1_design <- svydesign(ids = ~1, weights = ~weight, data = mod_id)

modid1 <- svyglm(formula = fecon2016 ~ POPDENS_CY, design = modid1_design)
summ(modid1)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = modid1_design))

```
* The econ factor score is predicted to increase (become more liberal) 3.825e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.282 (leans liberal)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00006, so it is significant to the p < 0.001

Condensed Conservative
```{r}
allcon_design <- svydesign(ids = ~1, weights = ~weight, data = all_con)

allcon1 <- svyglm(formula = fecon2016 ~ POPDENS_CY, design = allcon_design)
summ(allcon1)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = allcon_design))
```

Moderate Conservative
```{r}
#regress1_mcon <- lm(fecon2016 ~ POPDENS_CY, data = m_con)
#summary(regress1_mcon)

mcon1_design <- svydesign(ids = ~1, weights = ~weight, data = m_con)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = mcon1_design))
```
* The econ factor score is predicted to increase (become more liberal) 4.545e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.081 (leans liberal)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.08435, so it is significant at the p<0.1

Conservative
```{r}
#regress1_con <- lm(fecon2016 ~ POPDENS_CY, data = con)
#summary(regress1_con)

con1_design <- svydesign(ids = ~1, weights = ~weight, data = con)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = con1_design))
```
* The econ factor score is predicted to increase (become more liberal) 4.879e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 3.860 (conservative--big jump from moderate)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.2488, so it is not significant

---------------------------------------------------------

Strong Conservative
```{r}
#regress1_stcon <- lm(fecon2016 ~ POPDENS_CY, data = st_con)
#summary(regress1_stcon)

stcon1_design <- svydesign(ids = ~1, weights = ~weight, data = st_con)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = stcon1_design))
```
* The econ factor score is predicted to increase (become more liberal) 3.041e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 3.953
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.771, so it is not significant

========================================

All Dem
```{r}
alldem_design <- svydesign(ids = ~1, weights = ~weight, data = all_dem)

alldem1 <- svyglm(formula = fecon2016 ~ POPDENS_CY, design = alldem_design)
summ(alldem1)
```


Strong Democrat
```{r}
#regress1_stdem <- lm(fecon2016 ~ POPDENS_CY, data = st_dem)
#summary(regress1_stdem)

stdem1_design <- svydesign(ids = ~1, weights = ~weight, data = st_dem)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = stdem1_design))
```
* The econ factor score is predicted to increase (become more liberal) 1.577e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 8.547
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0142, so it is significant at the p<0.05

----------------------------------------------

Democrat
```{r}
#regress1_dem <- lm(fecon2016 ~ POPDENS_CY, data = dem)
#summary(regress1_dem)

dem1_design <- svydesign(ids = ~1, weights = ~weight, data = dem)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = dem1_design))
```
* The econ factor score is predicted to increase (become more liberal) 2.044e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.185
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0834, so it is slightly significant at the p<0.1

---------------------------------------------------

Moderate Democrat
```{r}
#regress1_mdem <- lm(fecon2016 ~ POPDENS_CY, data = m_dem)
#summary(regress1_mdem)

mdem1_design <- svydesign(ids = ~1, weights = ~weight, data = m_dem)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = mdem1_design))
```
* The econ factor score is predicted to increase (become more liberal) 3.487e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.928
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.000121, so it is significant at p<0.001

-------------------------------------------

Moderate Party ID
```{r}
#regress1_modparty <- lm(fecon2016 ~ POPDENS_CY, data = mod_party)
#summary(regress1_modparty)

modparty_design <- svydesign(ids = ~1, weights = ~weight, data = mod_party)

modparty1 <- svyglm(formula = fecon2016 ~ POPDENS_CY, design = modparty_design)
summ(modparty1)
```
* The econ factor score is predicted to increase (become more liberal) 2.409e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 5.546
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0111, so it is significant at the p<0.05

---------------------------------------

All Republicans
```{r}
allrep_design <- svydesign(ids = ~1, weights = ~weight, data = all_rep)

allrep1 <- svyglm(formula = fecon2016 ~ POPDENS_CY, design = allrep_design)
summ(allrep1)
```



Moderate Republican
```{r}
#regress1_mrep <- lm(fecon2016 ~ POPDENS_CY, data = m_rep)
#summary(regress1_mrep)

mrep1_design <- svydesign(ids = ~1, weights = ~weight, data = m_rep)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = mrep1_design))
```
* The econ factor score is predicted to decrease (become more conservative) -3.183e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 5.605 (slightly liberal)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.472, so it is not significant

-------------------------------------------------

Republican
```{r}
#regress1_rep <- lm(fecon2016 ~ POPDENS_CY, data = rep)
#summary(regress1_rep)

rep1_design <- svydesign(ids = ~1, weights = ~weight, data = rep)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = rep1_design))
```
* The econ factor score is predicted to increase (become more liberal) 6.485e-5 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 5.049
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.01216, so it is significant at the p<0.05

-------------------------------------------------------

Strong Republican
```{r}
#regress1_strep <- lm(fecon2016 ~ POPDENS_CY, data = st_rep)
#summary(regress1_strep)

strep1_design <- svydesign(ids = ~1, weights = ~weight, data = st_rep)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + factor(race) + gender + factor(educ), design = strep1_design))
```
* The econ factor score is predicted to increase (become more liberal) 0.0001239 (the largest effect) for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 0.492 (big jump from moderate republicans)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.000679, so it is significant at p<0.001

