---
title: "Model 1 Regress with Continuous Variables"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(haven)
library(gmodels)
library(survey)
```

# Notes



Multiple Linear Regression Example:
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results

## Model 1: Urban/rural (x = POPDENS_CY) effects policy positions (y = fecon2016) for each of the ideological and party identities

*demographic variables: "hispanic" "white", "white1", "black", "asian", "natamer", "otherrace", "gender", "fecon2016", "age18_24", "age25_34", "age35_44", "age45_54", "age55_64", "age65_74", "age75", "lessdiploma", "somecoll", "associate", "bachelors", "grad"



Strong Liberal
```{r}
wgt_dist <- combine2016 %>%
  group_by(partyid) %>%
  summarise()


#regress1_stlib <- lm(fecon2016 ~  POPDENS_CY + factor(race) + gender + factor(educ), data = st_lib)
                     
  # + hispanic + black + asian + natamer + otherrace + gender + age25_34 + age35_44 + age45_54 + age55_64 + age65_74 + age75 + somecoll + associate + bachelors + grad, data = st_lib)
summary(regress1_stlib)
```
* The econ factor score is predicted to increase 0.000007765 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the factor score is at 8.852
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.513, so it is not significant

Liberal
```{r}
regress1_lib <- lm(fecon2016 ~ POPDENS_CY, data = lib)
summary(regress1_lib)
```
* The econ factor score is predicted to decrease (become more conservative) -0.0000001798 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 7.915
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.983, so it is not significant

Moderate Liberal
```{r}
regress1_mlib <- lm(fecon2016 ~ POPDENS_CY, data = m_lib)
summary(regress1_mlib)
```
* The econ factor score is predicted to increase (become more liberal) 0.00002055 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.862
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.107, so it is not significant

Moderate Ideology
```{r}
regress1_modid <- lm(fecon2016 ~ POPDENS_CY, data = mod_id)
summary(regress1_modid)
```
* The econ factor score is predicted to increase (become more liberal) 0.00003715 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.184
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00107, so it is significant to the p < 0.01

Moderate Conservative
```{r}
regress1_mcon <- lm(fecon2016 ~ POPDENS_CY, data = m_con)
summary(regress1_mcon)
```
* The econ factor score is predicted to increase (become more liberal) 0.00007271 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 5.503
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0108, so it is significant at the p<0.05

Conservative
```{r}
regress1_con <- lm(fecon2016 ~ POPDENS_CY, data = con)
summary(regress1_con)
```
* The econ factor score is predicted to increase (become more liberal) 0.0001224 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 3.959
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00284, so it is significant at the p<0.01

---------------------------------------------------------

Strong Conservative
```{r}
regress1_stcon <- lm(fecon2016 ~ POPDENS_CY, data = st_con)
summary(regress1_stcon)
```
* The econ factor score is predicted to increase (become more liberal) 0.0001132 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 3.576
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.362, so it is not significant

========================================

Strong Democrat
```{r}
regress1_stdem <- lm(fecon2016 ~ POPDENS_CY, data = st_dem)
summary(regress1_stdem)
```
* The econ factor score is predicted to increase (become more liberal) 0.0000128 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 7.821
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0799, so it is slightly significant at the p<0.1

----------------------------------------------

Democrat
```{r}
regress1_dem <- lm(fecon2016 ~ POPDENS_CY, data = dem)
summary(regress1_dem)
```
* The econ factor score is predicted to increase (become more liberal) 0.00002099 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.801
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0925, so it is slightly significant at the p<0.1

---------------------------------------------------

Moderate Democrat
```{r}
regress1_mdem <- lm(fecon2016 ~ POPDENS_CY, data = m_dem)
summary(regress1_mdem)
```
* The econ factor score is predicted to increase (become more liberal) 0.00002852 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 7.140
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.115, so it is not significant

-------------------------------------------

Moderate Party ID
```{r}
regress1_modparty <- lm(fecon2016 ~ POPDENS_CY, data = mod_party)
summary(regress1_modparty)
```
* The econ factor score is predicted to increase (become more liberal) 0.00003248 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 6.13
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0855, so it is slightly significant at the p<0.1

---------------------------------------

Moderate Republican
```{r}
regress1_mrep <- lm(fecon2016 ~ POPDENS_CY, data = m_rep)
summary(regress1_mrep)
```
* The econ factor score is predicted to decrease (become more conservative) -0.00002748 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 4.761
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.586, so it is not significant

-------------------------------------------------

Republican
```{r}
regress1_rep <- lm(fecon2016 ~ POPDENS_CY, data = rep)
summary(regress1_rep)
```
* The econ factor score is predicted to increase (become more liberal) 0.00004634 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 4.794
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0404, so it is significant at the p<0.05

-------------------------------------------------------

Strong Republican
```{r}
regress1_strep <- lm(fecon2016 ~ POPDENS_CY, data = st_rep)
summary(regress1_strep)
```
* The econ factor score is predicted to increase (become more liberal) 0.0001599 for each one unit increase in population density (coefficient beta)
* When the predicted population density line is at 0, the predicted factor score is at 3.988
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.000255, so it is significant at p<0.001

