---
title: "Model 2 Regress with Continuous Variables"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(haven)
library(gmodels)
```

# Notes



Multiple Linear Regression Example:
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results

## Model 2: Urban/rural (x = POPDENS_CY) and District voting history (bluevote) effects policy positions (y = fecon2016) for each of the ideological and party identities

All Liberal
```{r}
alllib2 <- svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote, design = alllib_design)
summ(alllib2)
```


Strong Liberal
```{r}
#regress2_stlib <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = st_lib)
#summary(regress2_stlib)

stlib_design <- svydesign(ids = ~1, weights = ~weight, data = st_lib)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = stlib_design))
```
* The econ factor score is predicted to increase 0.00000712 for each one unit increase in population density (coefficient beta) and 0.00460138 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 9.29703761 (very liberal)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.36032164 (pop dens) and 0.52373942 (blue vote), so it is not significant

--------------------------

Liberal
```{r}
#regress2_lib <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = lib)
#summary(regress2_lib)

lib_design <- svydesign(ids = ~1, weights = ~weight, data = lib)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = lib_design))
```
* The econ factor score is predicted to increase 8.56e-6 for each one unit increase in population density (coefficient beta) and 0.00598960 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 9.077
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.359 (pop dens) and 0.389 (blue vote), so it is not significant

--------------------------
Moderate Liberal
```{r}
#regress2_mlib <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = m_lib)
#summary(regress2_mlib)

mlib_design <- svydesign(ids = ~1, weights = ~weight, data = m_lib)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = mlib_design))
```
* The econ factor score is predicted to increase 3.99e-5 for each one unit increase in population density (coefficient beta) and decrease -0.01160607 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 7.4891
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0015 (pop dens), which is significant at p<0.01, and 0.124 (blue vote), which is not significant

--------------------------

Moderate Ideology
```{r}
#regress2_modid <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = mod_id)
#summary(regress2_modid)
modid2 <- svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote, design = modid_design)
summ(modid2)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = modid_design))
```
* The econ factor score is predicted to increase 3.171e-5 for each one unit increase in population density (coefficient beta) and 0.00495553 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.07426671
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00255949 (pop dens), which is significant at the p<0.01, and 0.43805382 (blue vote) which is not significant

--------------------------

All Conservative
```{r}
allcon2 <- svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote, design = allcon_design)
summ(allcon2)
```


Moderate Conservative
```{r}
#regress2_mcon <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = m_con)
#summary(regress2_mcon)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = mcon_design))
```
* The econ factor score is predicted to increase 2.299e-5 for each one unit increase in population density (coefficient beta) and 0.00844369 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.7399 (slightly liberal)
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.49964630 (pop dens), not significant, and 0.21202238 (blue vote), no significant

--------------------------

Conservative
```{r}
#regress2_cons <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = con)
#summary(regress2_cons)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = con_design))
```
* The econ factor score is predicted to increase 6.767e-5 for each one unit increase in population density (coefficient beta) and decrease -0.00513076 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 4.102
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.17019395 (pop dens), not significant, and 0.53855139 (blue vote), not significant

--------------------------

Strong Conservative
```{r}
#regress2_stcon <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = st_con)
#summary(regress2_stcon)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = stcon_design))
```
* The econ factor score is predicted to increase 7.787e-5 for each one unit increase in population density (coefficient beta) and decrease -0.01456946 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.47900825 (pop dens) and 0.31887466 (blue vote), so it is not significant

===========================================

All Democrats
```{r}
alldem2 <- svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote, design = alldem_design)
summ(alldem2)
```



Strong Democrat
```{r}
#regress2_stdem <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = st_dem)
#summary(regress2_stdem)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = stdem_design))
```
* The econ factor score is predicted to increase 1.052e-5 for each one unit increase in population density (coefficient beta) and 4.83982e-3 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 7.479
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.5141 (pop dens), not significant, and 0.0869 (blue vote), which is slightly significant at the p<0.1

--------------------------

Democrat
```{r}
#regress2_dem <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = dem)
#summary(regress2_dem)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = dem_design))
```
* The econ factor score is predicted to increase 1.930e-5 for each one unit increase in population density (coefficient beta) and 0.00125058 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.15 (pop dens) and 0.86 (blue vote), so it is not significant

--------------------------

Moderate Democrat
```{r}
#regress2_mdem <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = m_dem)
#summary(regress2_mdem)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = mdem_design))
```
* The econ factor score is predicted to increase 2.529e-5 for each one unit increase in population density (coefficient beta) and 0.00796183 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.04631018 (pop dens), is significant, and 0.28287783 (blue vote), which is not significant 

--------------------------

Moderate Party
```{r}
#regress2_modparty <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = mod_party)
#summary(regress2_modparty)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = modparty_design))

modparty2 <- svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote, design = modparty_design)
summ(modparty2)
```
* The econ factor score is predicted to increase 3.236e-5 for each one unit increase in population density (coefficient beta) and decrease -0.00793043 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00069326 (pop dens), which is significant, and 0.29571397 (blue vote), which is not significant

--------------------------
All Republicans
```{r}
allrep2 <- svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote, design = allrep_design)
summ(allrep2)
```



Moderate Republican
```{r}
#regress2_mrep <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = m_rep)
#summary(regress2_mrep)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = mrep_design))
```
* The econ factor score is predicted to increase 3.34e-6 for each one unit increase in population density (coefficient beta) and decrease -0.00978053 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.96089986
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.94837567 (pop dens) and 0.43257455 (blue vote), so it is not significant

--------------------------

Republicans
```{r}
#regress2_rep <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = rep)
#summary(regress2_rep)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = rep_design))
```
* The econ factor score is predicted to increase 3.598e-5 for each one unit increase in population density (coefficient beta) and 0.01955334 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 3.966
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.19160221 (pop dens), not significant, and 0.03524530 (blue vote), which is significant at the p<0.05

--------------------------

Strong Republicans
```{r}
#regress2_strep <- lm(fecon2016 ~ POPDENS_CY + bluevote, data = st_rep)
#summary(regress2_strep)

summ(svyglm(formula = fecon2016 ~ POPDENS_CY + bluevote + factor(race) + gender + factor(educ), design = strep_design))
```
* The econ factor score is predicted to increase 1.3721e-4 for each one unit increase in population density (coefficient beta) and decrease -0.00351444 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 0.64934091
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.64934091 (pop dens), significant at the p<0.01, and 0.70554763 (blue vote), which is not significant
