---
title: "M3 Regress with Continuous"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(haven)
library(gmodels)
```

# Notes



Multiple Linear Regression Example:
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results

## Model 3: District voting history (bluevote) effects policy positions (y = fecon2016) for each of the ideological and party identities

Strong Liberal
```{r}
regress3_stlib <- lm(fecon2016 ~ bluevote, data = st_lib)
summary(regress3_stlib)
```
* The econ factor score is predicted to increase 0.003396 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 8.692
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.596 (blue vote), so it is not significant

--------------------------

Liberal
```{r}
regress3_lib <- lm(fecon2016 ~ bluevote, data = st_lib)
summary(regress3_lib)
```
* The econ factor score is predicted to increase 0.003396 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 8.692
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.596, so it is not significant

--------------------------

Moderate Liberal
```{r}
regress3_mlib <- lm(fecon2016 ~ bluevote, data = m_lib)
summary(regress3_mlib)
```
* The econ factor score is predicted to increase 0.005353 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.637
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.314, so it is not significant

--------------------------

Moderate Ideology
```{r}
regress3_modid <- lm(fecon2016 ~ bluevote, data = mod_id)
summary(regress3_modid)
```
* The econ factor score is predicted to increase 0.021548 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.233
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0000013, so it is significant at the p<0.001 level

--------------------------

Moderate Conservative
```{r}
regress3_mcon <- lm(fecon2016 ~ bluevote, data = m_con)
summary(regress3_mcon)
```
* The econ factor score is predicted to increase 0.017619 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 4.7716
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00294, so it is significant at the p<0.01 level

--------------------------

Conservative
```{r}
regress3_con <- lm(fecon2016 ~ bluevote, data = con)
summary(regress3_con)
```
* The econ factor score is predicted to increase 0.020729 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 3.188
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00161, so it is significant at the p<0.01 level

--------------------------

Strong Conservative
```{r}
regress3_stcon <- lm(fecon2016 ~ bluevote, data = st_con)
summary(regress3_stcon)
```
* The econ factor score is predicted to increase 0.01018 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 3.21798
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.464, so it is not significant

======================================

Strong Democrat
```{r}
regress3_stdem <- lm(fecon2016 ~ bluevote, data = st_dem)
summary(regress3_stdem)
```
* The econ factor score is predicted to increase 0.008042 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 7.426
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0182 (blue vote), so it is significant at the p<0.05

--------------------------

Democrat
```{r}
regress3_dem <- lm(fecon2016 ~ bluevote, data = dem)
summary(regress3_dem)
```
* The econ factor score is predicted to increase 0.011146 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.268
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0438, so it is significant at the p<0.05

--------------------------

Moderate Democrat
```{r}
regress3_mdem <- lm(fecon2016 ~ bluevote, data = m_dem)
summary(regress3_mdem)
```
* The econ factor score is predicted to increase 0.015752 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.415986
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00574, so it is significant at the p<0.01

--------------------------

Moderate Party
```{r}
regress3_modparty <- lm(fecon2016 ~ bluevote, data = mod_party)
summary(regress3_modparty)
```
* The econ factor score is predicted to increase 0.007167 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.852476
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.363, so it is not significant

--------------------------

Moderate Republican
```{r}
regress3_mrep <- lm(fecon2016 ~ bluevote, data = m_rep)
summary(regress3_mrep)
```
* The econ factor score is predicted to increase 0.00007608 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 4.731
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.993, so it is not significant

--------------------------

Republican
```{r}
regress3_rep <- lm(fecon2016 ~ bluevote, data = rep)
summary(regress3_rep)
```
* The econ factor score is predicted to increase 0.022088 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 3.860807
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00274, so it is significant at the p<0.01

--------------------------

Strong Republican
```{r}
regress3_strep <- lm(fecon2016 ~ bluevote, data = st_rep)
summary(regress3_strep)
```
* The econ factor score is predicted to increase 0.015945 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 3.45
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.0124, so it is significant at the p<0.05




