---
title: "M3 Regress with Continuous"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(haven)
library(gmodels)
```

# Notes



Multiple Linear Regression Example:
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results

## Model 3: District voting history (bluevote) effects policy positions (y = fecon2016) for each of the ideological and party identities

Strong Liberal
```{r}
#regress3_stlib <- lm(fecon2016 ~ bluevote, data = st_lib)
#summary(regress3_stlib)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = stlib_design))
```
* The econ factor score is predicted to increase 0.00612886 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 9.24905710
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.35682492 (blue vote), so it is not significant

--------------------------

All Liberal
```{r}
alllib3 <- svyglm(formula = fecon2016 ~ bluevote, design = alllib_design)
summ(alllib3)
```


Liberal
```{r}
#regress3_lib <- lm(fecon2016 ~ bluevote, data = st_lib)
#summary(regress3_lib)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = lib_design))
```
* The econ factor score is predicted to increase 0.00858240 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 8.89579890
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.14519488, so it is not significant

--------------------------

Moderate Liberal
```{r}
#regress3_mlib <- lm(fecon2016 ~ bluevote, data = m_lib)
#summary(regress3_mlib)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = mlib_design))
```
* The econ factor score is predicted to increase 0.00113310 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.84142058
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.88909985, so it is not significant

--------------------------

Moderate Ideology
```{r}
#regress3_modid <- lm(fecon2016 ~ bluevote, data = mod_id)
#summary(regress3_modid)

modid3 <- svyglm(formula = fecon2016 ~ bluevote, design = modid_design)

summ(modid3)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = modid_design))
```
* The econ factor score is predicted to increase 0.01147326 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.79516547
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.04694668, so it is significant

```{r}
allcon3 <- svyglm(formula = fecon2016 ~ bluevote, design = allcon_design)
summ(allcon3)
```

All Conservative

--------------------------

Moderate Conservative
```{r}
#regress3_mcon <- lm(fecon2016 ~ bluevote, data = m_con)
#summary(regress3_mcon)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = mcon_design))
```
* The econ factor score is predicted to increase 0.01060269 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.65582619
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.07181948, so it is slightly significant

--------------------------

Conservative
```{r}
#regress3_con <- lm(fecon2016 ~ bluevote, data = con)
#summary(regress3_con)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = con_design))
```
* The econ factor score is predicted to increase 0.00025167 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 3.84114521
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.97256801, so it is significant at the p<0.01 level

--------------------------

Strong Conservative
```{r}
#regress3_stcon <- lm(fecon2016 ~ bluevote, data = st_con)
#summary(regress3_stcon)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = stcon_design))
```
* The econ factor score is predicted to decrease -0.01078277 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 4.40601602
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.39545149, so it is not significant

======================================
All Democrats
```{r}
alldem3 <- svyglm(formula = fecon2016 ~ bluevote, design = alldem_design)
summ(alldem3)
```



Strong Democrat
```{r}
#regress3_stdem <- lm(fecon2016 ~ bluevote, data = st_dem)
#summary(regress3_stdem)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = stdem_design))
```
* The econ factor score is predicted to increase 0.00766531 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 8.17704135
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.13034270 (blue vote), so it is slightly significant

--------------------------

Democrat
```{r}
#regress3_dem <- lm(fecon2016 ~ bluevote, data = dem)
#summary(regress3_dem)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = dem_design))
```
* The econ factor score is predicted to increase 0.00623350 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.00105875
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.33421391, so it is not significant

--------------------------

Moderate Democrat
```{r}
#regress3_mdem <- lm(fecon2016 ~ bluevote, data = m_dem)
#summary(regress3_mdem)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = mdem_design))
```
* The econ factor score is predicted to increase 0.01508348 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 6.29694009
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.02639755, so it is significant at the p<0.05

--------------------------

Moderate Party
```{r}
#regress3_modparty <- lm(fecon2016 ~ bluevote, data = mod_party)
#summary(regress3_modparty)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = modparty_design))

modparty3 <- svyglm(formula = fecon2016 ~ bluevote, design = modparty_design)
summ(modparty3)
```
* The econ factor score is predicted to decrease -0.00199321 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.65275854
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.78384499, so it is not significant

--------------------------
All Republican
```{r}
allrep3 <- svyglm(formula = fecon2016 ~ bluevote, design = allrep_design)
summ(allrep3)
```


Moderate Republican
```{r}
#regress3_mrep <- lm(fecon2016 ~ bluevote, data = m_rep)
#summary(regress3_mrep)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = mrep_design))
```
* The econ factor score is predicted to decrease -0.00949184 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 5.95250699
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.37640274, so it is not significant

--------------------------

Republican
```{r}
#regress3_rep <- lm(fecon2016 ~ bluevote, data = rep)
#summary(regress3_rep)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = rep_design))
```
* The econ factor score is predicted to increase 0.02364000 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 4.11062381
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.00553721, so it is significant at the p<0.01

--------------------------

Strong Republican
```{r}
#regress3_strep <- lm(fecon2016 ~ bluevote, data = st_rep)
#summary(regress3_strep)

summ(svyglm(formula = fecon2016 ~ bluevote + factor(race) + gender + factor(educ), design = strep_design))
```
* The econ factor score is predicted to increase 0.00919940 for each one unit increase in district blue vote
* When the predicted population density line is at 0, the factor score is at 0.08602707
* The coefficient for the econ factor score has a P-value (Pr(>|t|)) = 0.25025018, so it is not significant




