---
title: "Regressions"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

# Regressions

Independent variable (x) = clutster (urban/rural classification)
Dependent variable (y) = Liberal issue answers

# Multiple Linear Regression Example
fit <- lm(y ~ x1 + x2 + x3, data=mydata)
summary(fit) # show results


## First: x = clust, y = fecon2016
```{r}
first <- lm(fecon2016 ~ clust, data = combine2016)

summary(first)

firstplot <- plot(fecon2016 ~ clust, data = combine2016)

ggplot(combine2016, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Second: x = clust, x = fecon2016 filtered by political ID
```{r}
# create new dataframes for each political ID
alllib <- filter(combine2016, libcon == c(6, 5, 4))

stlib <- filter(combine2016, libcon == 6) # STRONG LIBERAL

lib <- filter(combine2016, libcon == 5) # LIBERAL

mlib <- filter(combine2016, libcon == 4) # MODERATE LIBERAL

mod <- filter(combine2016, libcon == 3) # MODERATE

mcon <- filter(combine2016, libcon == 2) # MODERATE CONSERVATIVE

con <- filter(combine2016, libcon == 1) # CONSERVATIVE

scon <- filter(combine2016, libcon == 0) # STRONG CONSERVATIVE

allcon <- filter(combine2016, libcon == c(2, 1, 0))

# create new dataframes for party ID
sdem <- filter(combine2016, partyid == 6) # STRONG DEMOCRAT

srep <- filter(combine2016, partyid == 0) # STRONG REPUBLICAN
```

all liberal
```{r}
alllib_reg <- lm(fecon2016 ~ clust, data = alllib)

summary(alllib_reg)
```


strong liberal
```{r}
stlib_reg <- lm(fecon2016 ~ clust, data = stlib)

summary(stlib_reg)

plot(fecon2016 ~ clust, data = stlib)

ggplot(stlib, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Liberal
```{r}
lib_reg <- lm(fecon2016 ~ clust, data = lib)

summary(lib_reg)

plot(fecon2016 ~ clust, data = lib)

ggplot(lib, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Moderate Liberal
```{r}
mlib_reg <- lm(fecon2016 ~ clust, data = mlib)

summary(mlib_reg)

plot(fecon2016 ~ clust, data = mlib)

ggplot(mlib, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Moderate
```{r}
mod_reg <- lm(fecon2016 ~ clust, data = mod)

summary(mod_reg)

plot(fecon2016 ~ clust, data = mod)

ggplot(mod, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Moderate Conservative
```{r}
mcon_reg <- lm(fecon2016 ~ clust, data = mcon)

summary(mcon_reg)

plot(fecon2016 ~ clust, data = mcon)

ggplot(mcon, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Conservative
```{r}
con_reg <- lm(fecon2016 ~ clust, data = con)

summary(con_reg)

plot(fecon2016 ~ clust, data = con)

ggplot(con, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```
Strong Conservative
```{r}
scon_reg <- lm(fecon2016 ~ clust, data = scon)

summary(scon_reg)

plot(fecon2016 ~ clust, data = scon)

ggplot(scon, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```

All Conservative
```{r}
allcon_reg <- lm(fecon2016 ~ clust, data = allcon)

summary(allcon_reg)
```


Strong Democrat
```{r}
stlib_reg <- lm(fecon2016 ~ clust, data = stlib)

summary(stlib_reg)

plot(fecon2016 ~ clust, data = sdem)

ggplot(sdem, aes(x = clust, y = fecon2016)) +
  geom_point() +
  geom_smooth(method = "lm")
```



# Calculate frequency of mismatchers
```{r}

```

