---
title: "Variables"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
```

# Visualizing Variables

## Political ID

6 = Strong Liberal
.
0 = Strong Conservative
```{r}
ggplot(econ2016recode, aes(x = libcon)) + 
  geom_bar(stat = "count")
```

## Partisan Identification

6 = Strong Democrat 
.
0 = Strong Republican

```{r}
ggplot(econ2016recode, aes(x = partyid)) +
  geom_bar(stat = "count")
```


## Government services and spending scale

6 = govenrnment should provide more services
.
0 = government should provide fewer services

```{r}
ggplot(econ2016recode, aes(x = govservice)) +
  geom_bar(stat = "count")
```

## Medical Insurance Scale

6 = government insurance
.
0 = private insurance

```{r}
ggplot(econ2016recode, aes(x = medinsur)) +
  geom_bar(stat = "count")
```



    medinsur, # MEDICAL INSURANCE SCALE: 6 = GOV INSUANCE ... 0 = PRIVATE INSURANCE
    fedgun, # 2 = GUN PURCHASE EASIER, 1 = THE SAME, 0 = GUN PURCHASE MORE DIFFICULT
    govjob, # GOV JOB SCALE: 6 = GOV GUARANTEES JOBS ... 0 = GET JOBS ON OWN
    govblacks, # AID TO BLACKS SCALE: 6 = GOV SHOULD HELP BLACKS ... 0 = BLACKS HELP SELVES
    ssocsec, # 1 = INCREASED SPENDING ON SOCSEC, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sschools, # 1 = INCREASED SPENDING ON SCHOOLS, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sscience, # 1 = INCREASED SPENDING ON SCIENCE, 0 = KEEP SAME, -1 DECREASED SPENDING
    swelfare, # 1 = INCREASED SPENDING ON WELFARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    schildcare, # 1 = INCREASED SPEND ON CHILD CARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    spoor, # 1 = INCREASED SPEND ON POOR, 0 = KEEP SAME, -1 = DECREASED SPENDING
    senviron, # 1 = INCREASED SPEND ON ENVIRONMENT, 0 = KEEP SAME, -1 = DECREASED,
    govinequality, # 2 = R SUPPORT GOV EFFORTS TO REDUCE INEQUALITY, 1 = NEUTRAL, 0 = OPPOSE
    
    
# Cross Tabulations

```{r}
xtabs( ~ libcon + partyid, data = econ2016recode)
```



caseid,
    stfips, # STATE FIPS CODE
    stabbrev, # STATE ABBREVIATION
    congdist, # CONGRESSIONAL DISTRICT NUMBER
    libcon, # POLITICAL ID (FORCED): 6 = strong liberal ... 0 = strong conservative 
    partyid, # PARTISAN ID: 6 = STRONG REP ... 0 = STRONG DEM
    govservice, # GOV SERVICES SCALE: 6 = GOV SHOULD PROVIDE MORE SERVICES
    medinsur, # MEDICAL INSURANCE SCALE: 6 = GOV INSUANCE ... 0 = PRIVATE INSURANCE
    fedgun, # 2 = GUN PURCHASE EASIER, 1 = THE SAME, 0 = GUN PURCHASE MORE DIFFICULT
    govjob, # GOV JOB SCALE: 6 = GOV GUARANTEES JOBS ... 0 = GET JOBS ON OWN
    govblacks, # AID TO BLACKS SCALE: 6 = GOV SHOULD HELP BLACKS ... 0 = BLACKS HELP SELVES
    ssocsec, # 1 = INCREASED SPENDING ON SOCSEC, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sschools, # 1 = INCREASED SPENDING ON SCHOOLS, 0 = KEEP SAME, -1 = DECREASED SPENDING
    sscience, # 1 = INCREASED SPENDING ON SCIENCE, 0 = KEEP SAME, -1 DECREASED SPENDING
    swelfare, # 1 = INCREASED SPENDING ON WELFARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    schildcare, # 1 = INCREASED SPEND ON CHILD CARE, 0 = KEEP SAME, -1 = DECREASED SPENDING
    spoor, # 1 = INCREASED SPEND ON POOR, 0 = KEEP SAME, -1 = DECREASED SPENDING
    senviron, # 1 = INCREASED SPEND ON ENVIRONMENT, 0 = KEEP SAME, -1 = DECREASED,
    gwaction, # 6 = GOV SHOULD BE DOING GREAT DEAL MORE FOR GLOBAL WARMING ... 0 = LESS
    govinequality, # 2 = R SUPPORT GOV EFFORTS TO REDUCE INEQUALITY, 1 = NEUTRAL, 0 = OPPOSE
    shealthcare7, # 6 = SUPPORT STRONG INCREASE IN HEALTH CARE SPEND, 0 = STRONG DECREASE
    taxmillion, # 2 = SUPPORTS INCREASING TAXES ON MILLIONAIRES, 1 = NEUTRAL, 0 = OPPOSE
    govprob, # 1 = GOV DOING TOO MUCH, 0 = PROBLEMS ARE BIGGER
    fmarket, # 1 = FREE MARKET CAN HANDLE PROBLEMS, 0 = GOV NEEDED TO SOLVE PROBLEMS
    govless, # 1 = LESS GOV THE BETTER, 0 = GOV SHOULD DO MORE THINGS
    gregbus, # 4 = A GREAT DEAL OF REGULATION IS GOOD FOR SOCIETY ... 0 = NONE AT ALL